---
title: "FRP_LTMsonde analysis"
author: "DMC"
date: "5/25/2022"
output: html_document
---


This file contains a preliminary view of the long-term sonde deployments for Yolo Flyway Farms and Decker (breach + pool)
OLD - DMC210722 - this was modified to include the new compiled data perfomed by DMC on 210722
DMC220526 - this was modified to work with the new compiled data performed by DMC on 220525

```{r}
rm(list = ls())

df_DeckB <- data.frame(read.csv(file = "DMC_CompileDataRaw4R_DeckerBreach.csv"))
df_DeckB$Site.Name <- c("Decker Breach")
df_DeckP <- data.frame(read.csv(file = "DMC_CompileDataRaw4R_DeckerPool.csv"))
df_DeckP$Site.Name <- c("Decker Pool")
df_YoloF <- data.frame(read.csv(file = "DMC_CompileDataRaw4R_YoloFlyway.csv"))
df_YoloF$Site.Name <- c("Yolo Flyway Farm")
df <- rbind.data.frame(df_DeckB,df_DeckP,df_YoloF)
colnames(df) <- c("SondeName","Date","Time","tFracSec","Site","ChlRFU","Depthm","fDOMRFU","DOsat","DOmgL","SPC","PCRFU","Turb","TempC","WiperPos")
df$dts <- paste(df$Date,df$Time,sep = " ")
df$dts <- as.POSIXct(strptime(df$dts, format = "%m/%d/%Y %H:%M:%S"))
df$Chlconc <- c(rep(NA,length(df$SondeName)))
df$fDOMconc <- c(rep(NA,length(df$SondeName)))

save(df, file = "FRP_LTMsonde_220526.RData")
```

This chunk will replicate the work by Mandy (again). For Decker
```{r}
library(SWMPr)
library(ggplot2)
library(reshape2)
library(viridis)
library(plyr)
library(scales)
library(gridExtra)

rm(list = ls())


load("FRP_LTMsonde_220526.RData")
load("ExtLTM_CompleteMerge.RData") ###DMC220601: this is a huge file with all data from every nearby sonde

df <- df[which(df$dts >= as.POSIXct(strptime("2021-01-01 00:00", format = "%Y-%m-%d")) & 
                 df$dts <= as.POSIXct(strptime("2021-12-31 23:45", format = "%Y-%m-%d"))),]
df$Turb[which(df$Turb > 1000)] <- NA ###DMC220713: Turbidity sensor is only rated up to 1000 so any values above it must be discarded. The high calibration standard used is ~100 so any values above that are suspect

df$ChlRFU[which(df$ChlRFU > 100)] <- NA ###DMC220713: Chl sensor is only rated up to 100 RFU so any values above it must be discarded.
df$PCRFU[which(df$PCRFU > 100 | df$PCRFU < 0)] <- NA ###DMC220713: Phycocyanin sensor is only rated up to 100 RFU so any values above it must be discarded. Any values below 0 must be discarded too
df$fDOMRFU[which(df$fDOMRFU < 0)] <- NA ###DMC220713: FDOM sensor is only rated up to 100 RFU so any values above it must be discarded. Any values below 0 must be discarded too

unique(dfAll$site)
dfAll <- dfAll[which(dfAll$site %in% c("SacSherman_CDEC") & # "SDI_USGS","Emmaton_CDEC" ###DMC220713: these stations did not have data
                       dfAll$dts >= as.POSIXct(strptime("2021-01-01 00:00", format = "%Y-%m-%d")) & 
                       dfAll$dts <= as.POSIXct(strptime("2021-12-31 23:45", format = "%Y-%m-%d"))),]

dat <- df[,c("Site","dts","TempC","SPC","Turb","DOmgL","ChlRFU","PCRFU","fDOMRFU")]
dat[,10:11] <- as.numeric(NA)
colnames(dat)[10:11] <- c("fdomConc","velocity")

dfAll <- dfAll[,-5]
dfAll[,10:11] <- as.numeric(NA)
dfAll <- dfAll[,c(1:7,10,11,8,9)]
colnames(dfAll) <- colnames(dat)

#dfAll$datetime <- as.character(dfAll$dts)
#dfAll$dts <- NA
#dfAll$dts <- as.POSIXct(strptime(dfAll$datetime, format = "%Y-%m-%d %H:%M:%S", tz = "PST"))
#dfAll <- dfAll[,-8]
dfAll$ChlRFU <- as.numeric(dfAll$ChlRFU)
dfAll$PCRFU <- as.numeric(dfAll$PCRFU)
dfAll$fDOMRFU <- as.numeric(dfAll$fDOMRFU)

dfAll$ChlRFU[which(dfAll$ChlRFU > 400)] <- NA ###DMC220713: Chl sensor is only rated up to 400 ug/L so any values above it must be discarded.

dat3 <- rbind.data.frame(dat,dfAll)
colnames(dat3)[1:2] <- c("Station.Code","datetimestamp")


#dat <- df ### DMC: need to figure out the 8 observations that do not have appropriate datetimestamp #ddd <- df[which(is.na(df$dts == TRUE)),]
#dat2 <- dat[,c(5,16,14,11,10,13,6,17,8,18,12,15)]
#dat2 <- dat2[,c(1:5,9)]
#colnames(dat2)[5:6] <- c("Turb","DOmgL")
#dfSDI <- dfSDI[,c(1:4,6,5,12,8,13,9,14,15)]
#dfToe <- dfToe[,c(1:4,6,5,13,8,14,9,15,16)]
#dat3 <- rbind.data.frame(dat2,dfSDI,dfToe)
#dat3$dts <- as.POSIXct(strptime(dat3$dts, format = "%Y-%m-%d %H:%M:%S"))
#colnames(dat3)[1:2] <- c("Station.Code","datetimestamp")


#dat3 <- dat3[which(dat3$datetimestamp >= as.POSIXct(strptime("2019-01-01 00:00",format = "%Y-%m-%d %H:%M")) & dat3$datetimestamp <= as.POSIXct(strptime("2020-12-31 23:45",format = "%Y-%m-%d %H:%M"))),]

#baddpT <- dat3[which(dat3$SPC < 150 & dat3$Station.Code =="Decker Pool"),]
#dat3 <- dat3[-which(dat3$SPC < 150 & dat3$Station.Code =="Decker Pool"),] ###DMC210721: I added this line because values less than 150 meant that the sonde was not measuring within the water column

#badWP <- dat3[which(dat3$WiperPos < 1.1 | dat3$WiperPos > 1.3),]
#dat3 <- dat3[-which(dat3$WiperPos < 1.1 | dat3$WiperPos > 1.3),]

dat3 <- swmpr(dat3, meta_in = FALSE)
attr(dat3,'timezone')<-"UTC"

agg_dat_sub <- aggreswmp(dat3, by = 'hours', 
                         params = c('Station.Code','TempC','SPC','Turb','DOmgL','ChlRFU','fDOMRFU','fdomConc','PCRFU'), aggs_out = T)
  #params = c('Station.Code','TempC','SPC','Turb','DOmgL','ChlRFU','Chlconc','fDOMRFU','fDOMconc','PCRFU'), aggs_out = T)

summH <- ddply(agg_dat_sub, c("Station.Code","datetimestamp"), summarise,
               Tempbar = mean(TempC),
               SPCbar = mean(SPC),
               Turbbar = mean(Turb),
               DObar = mean(DOmgL),
               ChlRFUbar = mean(ChlRFU),
               #Chlconcbar = mean(Chlconc),
               fDOMRFUbar = mean(fDOMRFU),
               fDOMconcbar = mean(fdomConc),
               PCbar = mean(PCRFU)
               )
agg_dat_sub <- summH

to_plo_sub <- melt(agg_dat_sub, id.var = c('Station.Code','datetimestamp'))
to_plo_sub$dts <- as.POSIXct(strptime(as.character(to_plo_sub$datetimestamp),format = "%Y-%m-%d"))
to_plo_sub$Station.Code <- factor(to_plo_sub$Station.Code, levels = c("Decker Breach", "Decker Pool", "SDI_USGS", "Emmaton_CDEC", "SacSherman_CDEC"))#,
                                  #labels = c("P","B","S","Y","T"))
to_plo_sub <- to_plo_sub[which(is.na(to_plo_sub$datetimestamp)==FALSE),]

to_plo_sub$ord <- as.numeric(to_plo_sub$Station.Code)
to_plo_sub <- to_plo_sub[order(to_plo_sub$ord),]

unique(to_plo_sub$Station.Code)
yolo <- c("Yolo Flyway Farm","Toe Drain")
decker <- c("Decker Breach","Decker Pool","SacSherman_CDEC") #,"SDI_USGS","Emmaton_CDEC" ###DMC220713: these stations did not have data

xdtsDeck <- to_plo_sub$datetimestamp[which(to_plo_sub$Station.Code == "Decker Pool")]
xdtsDeck2 <- range(xdtsDeck)
#xdtsDeck2[1] <- as.POSIXct(strptime("2022-01-01 00:00", format = "%Y-%m-%d %H:%M"),tz = "UTC")
#xdtsYolo <- to_plo_sub$datetimestamp[which(to_plo_sub$Station.Code == "Yolo Flyway Farm")]

mycol <- (viridis_pal(option = "H")(56))[c(24,44,33)]
mycol[3] <- c("black")
mysh <- c(25,21,21)
myps <- c(1.5,1.3,1)
myalf <- c(0.5,0.5,0.7)


plo_agg_subT <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% decker & to_plo_sub$datetimestamp %in% xdtsDeck & to_plo_sub$variable == "Tempbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) + #(to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2])
  geom_point(colour = "black") +#, shape = 21
  geom_hline(yintercept=25.4) + ###DMC: "Swanson C, Reid T, Young PS, Cech Jr JJ. 2000. Comparative environmental tolerances of threatened delta smelt (Hypomesus transpacificus) and introduced Wakasagi (H. nipponensis) in an altered California estuary. Oecologia 123(3):384-390
  geom_hline(yintercept=24, linetype="dashed") + ###DMC: reference is "Rich A.A. (1987). Report on studies conducted by Sacramento County to determine the temperatures which optimize growth and survival in juvenile chinook salmon (Onchorhynchus tshawwytscha). McDonough, Holland, & Allen, Sacramento, CA"
  scale_fill_manual(values = mycol,labels = c("Breach","Interior","Sacramento\nRiver")) + # ,"Sac@Decker","EMM","Sac@Sherman"
  scale_shape_manual(values = mysh,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_size_manual(values = myps,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior","Sacramento\nRiver")) +
  theme_classic() +
  xlab("Date") +
  ylab("Temperature (\u00b0C)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


plo_agg_subDO <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% decker & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "DObar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code,shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +
  #geom_hline(yintercept=2.5) + 
  #geom_hline(yintercept=4.6, linetype="dashed") + 
  scale_fill_manual(values = mycol,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_shape_manual(values = mysh,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_size_manual(values = myps,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior","Sacramento\nRiver")) +
  theme_classic() +
  xlab("Date") +
  ylab("Dissolved Oxygen (mg/L)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

plo_agg_subSPC <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% decker & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "SPCbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +
  #geom_hline(yintercept=2.5) + 
  #geom_hline(yintercept=4.6, linetype="dashed") + 
  scale_fill_manual(values = mycol,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_shape_manual(values = mysh,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_size_manual(values = myps,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior","Sacramento\nRiver")) +
  #ylim(150,650)+
  theme_classic() +
  xlab("Date") +
  ylab("Specific Conductivity (\u00B5S/cm)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
pl2 <- plo_agg_subSPC + annotation_custom(grob = ggplotGrob(plo_agg_subSPC +ylim(0,2100) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         xmin = as.POSIXct(strptime("2020-01-05",format = "%Y-%m-%d")),
                                         #xmax = as.POSIXct(strptime("2020-01-01",format = "%Y-%m-%d")), 
                                         ymin = 375, ymax = 675)


###DMC220713: Turbidity sensor is only rated up to 1000 so any values above it must be discarded. The high calibration standard used is ~100 so any values above that are suspect
plo_agg_subTu <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% decker & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "Turbbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +
  geom_hline(yintercept=12, linetype = "dashed")+ #Grimaldo LF, Sommer T, Van Ark N, Jones G, Holland E, Moyle PB, Smith P, Herbold B. 2009a. Factors affecting fish entrainment into massive water diversions in a freshwater tidal estuary: Can fish losses be managed? N Am J Fish Manage 29:1253-1270.
  geom_hline(yintercept=80) + # Can also use this for the above '12' turbidity value too: Hasenbein M, Fangue NA, Geist J, Komoroske LM, Truong J, McPherson R, Connon RE (2016) Assessments at multiple levels of biological organization allow for an integrative determination of physiological tolerances to turbidity in an endangered fish species. Conserv Physiol 4: doi:10.1093/conphys/cow004.
  scale_fill_manual(values = mycol,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_shape_manual(values = mysh,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_size_manual(values = myps,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior","Sacramento\nRiver")) +
  #ylim(0,400)+
  theme_classic() +
  xlab("Date") +
  ylab("Turbidity (FNU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

pl2 <- plo_agg_subTu + annotation_custom(grob = ggplotGrob(plo_agg_subTu +ylim(0,NA) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         #xmin = as.POSIXct(strptime("2020-01-10",format = "%Y-%m-%d")),
                                         xmax = as.POSIXct(strptime("2020-03-15",format = "%Y-%m-%d")), 
                                         ymin = 200, ymax = 425)

###DMC210723: pick up here... wiper was down for Decker Breach prior to 200107 ###DMC210727: omitted the data for Decker Breach prior to 20
deckerOnly <- decker[1:2]
#plo_agg_subChl <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
plo_agg_subChl <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & to_plo_sub$variable == "ChlRFUbar" & to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +
  scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
  scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior")) +
  theme_classic() +
  #ylim(0,175) +
  xlab("Date") +
  ylab("Chlorophyll a (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
pl2 <- plo_agg_subChl + annotation_custom(grob = ggplotGrob(plo_agg_subChl +ylim(0,2) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         xmin = as.POSIXct(strptime("2021-08-10",format = "%Y-%m-%d")),
                                         #xmax = as.POSIXct(strptime("2020-01-01",format = "%Y-%m-%d")), 
                                         ymin = 21, ymax = 43)

sac <- decker[3]
plo_agg_subChlsac <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% sac & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[3],labels = c("Sac.\nRiver   "))+ 
  scale_shape_manual(values = mysh[3],labels = c("Sac.\nRiver   ")) +
  scale_size_manual(values = myps[3],labels = c("Sac.\nRiver   ")) +
  theme_classic() +
  xlab("Date") +
  ylab("Chlorophyll a (\u00B5g/L)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
gridExtra::grid.arrange(arrangeGrob(pl2, plo_agg_subChlsac,nrow = 2), ncol =1)
pl2sac <- plo_agg_subChlsac + annotation_custom(grob = ggplotGrob(plo_agg_subChlsac +ylim(0,10) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         xmin = as.POSIXct(strptime("2021-08-10",format = "%Y-%m-%d")),
                                         #xmax = as.POSIXct(strptime("2020-01-01",format = "%Y-%m-%d")), 
                                         ymin = 50, ymax = 130)
gridExtra::grid.arrange(arrangeGrob(pl2, pl2sac,nrow = 2), ncol =1)

#x <- seq(0,100)
#y <- seq(0,400,by=4)
#dfCHLRFU <- data.frame(x,y)
#plot(x,y)

plo_agg_subChlBoth <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(data = to_plo_sub[which(to_plo_sub$Station.Code %in% sac & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value-1), fill = mycol[3], shape = mysh[3], size = myps[3]) +
  geom_point(colour = "black") +
  scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
  scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior")) +
  scale_y_continuous(sec.axis = sec_axis(~.-1, name = "Chlorophyll a (\u00B5g/L)"))+
  theme_classic() +
  ylim(0,5) +
  xlab("Date") +
  ylab("Chlorophyll a (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
pl2 <- plo_agg_subChl + annotation_custom(grob = ggplotGrob(plo_agg_subChl +ylim(0,175) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         xmin = as.POSIXct(strptime("2020-01-10",format = "%Y-%m-%d")),
                                         #xmax = as.POSIXct(strptime("2020-01-01",format = "%Y-%m-%d")), 
                                         ymin = 1.5, ymax = 5.2)



deckerOnly <- decker[1:2]
plo_agg_subPC <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "PCbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  #geom_hline(yintercept=12, linetype = "dashed")+ #Grimaldo LF, Sommer T, Van Ark N, Jones G, Holland E, Moyle PB, Smith P, Herbold B. 2009a. Factors affecting fish entrainment into massive water diversions in a freshwater tidal estuary: Can fish losses be managed? N Am J Fish Manage 29:1253-1270.
  #geom_hline(yintercept=80) + # Can also use this for the above '12' turbidity value too: Hasenbein M, Fangue NA, Geist J, Komoroske LM, Truong J, McPherson R, Connon RE (2016) Assessments at multiple levels of biological organization allow for an integrative determination of physiological tolerances to turbidity in an endangered fish species. Conserv Physiol 4: doi:10.1093/conphys/cow004.
  scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
  scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
  #scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  #ylim(0,25) +
  #theme(axis.text.x = element_text(size = 24)) +
  #theme(axis.text=element_text(size=24)) #+
  #theme(strip.background = element_blank(),strip.text.y = element_blank(),strip.text = element_blank())#+
  xlab("Date") +
  ylab("Phycocyanin (RFU)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
pl2 <- plo_agg_subPC + annotation_custom(grob = ggplotGrob(plo_agg_subPC +ylim(0,NA) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         #xmin = as.POSIXct(strptime("2020-01-10",format = "%Y-%m-%d")),
                                         xmax = as.POSIXct(strptime("2020-03-15",format = "%Y-%m-%d")), 
                                         ymin = 1.7, ymax = 5.2)

deckerOnly <- decker[1:2]
plo_agg_subfdom <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "fDOMRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
  scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
  theme_classic() +
  #ylim(0,5) +
  xlab("Date") +
  ylab("Fluorescent Dissolved\nOrganic Matter (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


sac <- decker[3]
plo_agg_subfdomsac <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% sac & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "fDOMconcbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[3],labels = c("Sac.\nRiver   "))+ 
  scale_shape_manual(values = mysh[3],labels = c("Sac.\nRiver   ")) +
  scale_size_manual(values = myps[3],labels = c("Sac.\nRiver   ")) +
  theme_classic() +
  xlab("Date") +
  ylab("Fluorescent Dissolved\nOrganic Matter (mg/L as QSE)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


gridExtra::grid.arrange(arrangeGrob(plo_agg_subfdom, plo_agg_subfdomsac,nrow = 2), ncol =1)

sites <- c(yolo, decker)
p <- list()
for(i in seq_along(sites)){
  df <- agg_dat_subD[which(agg_dat_subD$Station.Code == sites[i]),]
  dfT95 <- aggregate(TempC ~ datetimestamp, data = df, FUN = quantile, probs  = 0.95)
  dfT95$qua <- c("pct95")
  dfT95$lt <- c("dotted")
  dfT50 <- aggregate(TempC ~ datetimestamp, data = df, FUN = quantile, probs  = 0.50)
  dfT50$qua <- c("median")
  dfT50$lt <- c("solid")
  dfT05 <- aggregate(TempC ~ datetimestamp, data = df, FUN = quantile, probs  = 0.05)
  dfT05$qua <- c("pct5")
  dfT05$lt <- c("dashed")
  dfD95 <- aggregate(DOmgL ~ datetimestamp, data = df, FUN = quantile, probs  = 0.95)
  dfD95$qua <- c("pct95")
  dfD95$lt <- c("dotted")
  dfD50 <- aggregate(DOmgL ~ datetimestamp, data = df, FUN = quantile, probs  = 0.50)
  dfD50$qua <- c("median")
  dfD50$lt <- c("solid")
  dfD05 <- aggregate(DOmgL ~ datetimestamp, data = df, FUN = quantile, probs  = 0.05)
  dfD05$qua <- c("pct5")
  dfD05$lt <- c("dashed")
  dfTu95 <- aggregate(Turb ~ datetimestamp, data = df, FUN = quantile, probs  = 0.95)
  dfTu95$qua <- c("pct95")
  dfTu95$lt <- c("dotted")
  dfTu50 <- aggregate(Turb ~ datetimestamp, data = df, FUN = quantile, probs  = 0.50)
  dfTu50$qua <- c("median")
  dfTu50$lt <- c("solid")
  dfTu05 <- aggregate(Turb ~ datetimestamp, data = df, FUN = quantile, probs  = 0.05)
  dfTu05$qua <- c("pct5")
  dfTu05$lt <- c("dashed")
  dfT <- rbind.data.frame(dfT95,dfT50,dfT05)
  dfT$variable <- "TempC"
  colnames(dfT)[2] <- c("value")
  dfT$Site <- sites[i]
  dfD <- rbind.data.frame(dfD95,dfD50,dfD05)
  dfD$variable <- "DOmgL"
  dfD$Site <- sites[i]
  colnames(dfD)[2] <- c("value")
  dfTu <- rbind.data.frame(dfTu95,dfTu50,dfTu05)
  dfTu$variable <- "Turb"
  colnames(dfTu)[2] <- c("value")
  dfTu$Site <- sites[i]
  p[[i]] <- rbind.data.frame(dfT,dfD,dfTu)
}
names(p) <- sites
to_plo2 <- do.call(rbind.data.frame, p)

xdtsDeck2 <- to_plo2$datetimestamp[which(to_plo2$Site == "Decker Breach")]
xdtsYolo2 <- to_plo2$datetimestamp[which(to_plo2$Site == "Yolo Flyway Farm")]

plo_stat <- ggplot(to_plo2[which(to_plo2$Site %in% yolo & to_plo2$datetimestamp %in% xdtsYolo2),], aes(x = datetimestamp, y = value, colour = Site, linetype = lt)) +
  geom_line() +
  facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() 



to_plo3 <- dcast(to_plo2,datetimestamp+Site+variable ~qua)
to_plo3$variable <- factor(to_plo3$variable, levels = c("TempC","DOmgL","Turb"), labels = c("Temperature (C)","Dissolved Oxygen (mg/L)","Turbidity (FNU)"))
plo_stat2 <- ggplot(to_plo3[which(to_plo3$Site %in% decker & to_plo3$datetimestamp %in% xdtsDeck2),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  theme(axis.title.y = element_blank())

plo_stat2 <- ggplot(to_plo3[which(to_plo3$Site %in% yolo & to_plo3$datetimestamp %in% xdtsYolo2),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  theme(axis.title.y = element_blank())


### Feb21 to Mar16 had no sondes
skipS <- c(as.POSIXct(strptime(c('2020-02-21 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-12 04:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-21 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-12 04:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-21 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-12 04:00:00'),format = "%Y-%m-%d %H:%M")))
skipE <- c(as.POSIXct(strptime(c('2020-03-18 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-13 16:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-03-18 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-13 16:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-03-18 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-13 16:00:00'),format = "%Y-%m-%d %H:%M")))
valmax <- c(23,23,12,12,400,400)#max(to_plo3$pct95[which(to_plo3$variable== "Temperature (C)")])
valmin <- c(5,5,5,5,0,0)#min(to_plo3$pct5[which(to_plo3$variable== "Temperature (C)")])
varSkip <- c("temp","temp","do","do","turb","turb")
dfBox <- data.frame(skipS,skipE,valmax,valmin, varSkip)

plo_stat4 <- ggplot(to_plo3[which(to_plo3$Site %in% decker & to_plo3$datetimestamp %in% xdtsDeck2 & to_plo3$variable=="Temperature (C)"),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  geom_hline(yintercept=25.4) + 
  geom_hline(yintercept=24, linetype="dashed") + 
  geom_rect(data = dfBox[which(dfBox$varSkip == "temp"),], aes(xmin = skipS, xmax = skipE, ymin = valmin, ymax = valmax),color = "white",fill="white")+
  scale_color_manual(values = mycol,labels = c("Pool","Breach","Channel")) +
  #scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  xlab("Date") +
  ylab("Temperature (C)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

plo_stat5 <- ggplot(to_plo3[which(to_plo3$Site %in% decker & to_plo3$datetimestamp %in% xdtsDeck2 & to_plo3$variable=="Dissolved Oxygen (mg/L)"),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  geom_hline(yintercept=2.5) + 
  geom_hline(yintercept=4.6, linetype="dashed") + 
  geom_rect(data = dfBox[which(dfBox$varSkip == "do"),], aes(xmin = skipS, xmax = skipE, ymin = valmin, ymax = valmax),color = "white",fill="white")+
  scale_color_manual(values = mycol,labels = c("Pool","Breach","Channel")) +
  scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  xlab("Date") +
  ylab("Dissolved Oxygen (mg/L)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

plo_stat6 <- ggplot(to_plo3[which(to_plo3$Site %in% decker & to_plo3$datetimestamp %in% xdtsDeck2 & to_plo3$variable=="Turbidity (FNU)"),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  geom_rect(data = dfBox[which(dfBox$varSkip == "turb"),], aes(xmin = skipS, xmax = skipE, ymin = valmin, ymax = valmax),color = "white",fill="white")+
  geom_hline(yintercept=12)+
  geom_hline(yintercept=80) + 
  scale_color_manual(values = mycol,labels = c("Pool","Breach","Channel")) +
  scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  xlab("Date") +
  ylab("Turbidity (FNU)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

```


For Yolo
```{r}
library(SWMPr)
library(ggplot2)
library(reshape2)
library(viridis)
library(plyr)
library(scales)
library(gridExtra)

rm(list = ls())


load("FRP_LTMsonde_220526.RData")
load("ExtLTM_CompleteMerge.RData") ###DMC220601: this is a huge file with all data from every nearby sonde

df <- df[which(df$dts >= as.POSIXct(strptime("2021-01-01 00:00", format = "%Y-%m-%d")) & 
                 df$dts <= as.POSIXct(strptime("2021-12-31 23:45", format = "%Y-%m-%d"))),]

unique(dfAll$site)
dfAll <- dfAll[which(dfAll$site %in% c("SDI_USGS","TOE_USGS","LIB_USGS") & 
                       dfAll$dts >= as.POSIXct(strptime("2021-01-01 00:00", format = "%Y-%m-%d")) & 
                       dfAll$dts <= as.POSIXct(strptime("2021-12-31 23:45", format = "%Y-%m-%d"))),]

dat <- df[,c("Site","dts","TempC","SPC","Turb","DOmgL","ChlRFU","PCRFU","fDOMRFU")]
dat[,10:11] <- as.numeric(NA)
colnames(dat)[10:11] <- c("fdomConc","velocity")

dfAll <- dfAll[,-5]
dfAll[,10:11] <- as.numeric(NA)
dfAll <- dfAll[,c(1:7,10,11,8,9)]
colnames(dfAll) <- colnames(dat)

#dfAll$datetime <- as.character(dfAll$dts)
#dfAll$dts <- NA
#dfAll$dts <- as.POSIXct(strptime(dfAll$datetime, format = "%Y-%m-%d %H:%M:%S", tz = "PST"))
#dfAll <- dfAll[,-8]
dfAll$ChlRFU <- as.numeric(dfAll$ChlRFU)
dfAll$PCRFU <- as.numeric(dfAll$PCRFU)
dfAll$fDOMRFU <- as.numeric(dfAll$fDOMRFU)
dat3 <- rbind.data.frame(dat,dfAll)
colnames(dat3)[1:2] <- c("Station.Code","datetimestamp")


#dat <- df ### DMC: need to figure out the 8 observations that do not have appropriate datetimestamp #ddd <- df[which(is.na(df$dts == TRUE)),]
#dat2 <- dat[,c(5,16,14,11,10,13,6,17,8,18,12,15)]
#dat2 <- dat2[,c(1:5,9)]
#colnames(dat2)[5:6] <- c("Turb","DOmgL")
#dfSDI <- dfSDI[,c(1:4,6,5,12,8,13,9,14,15)]
#dfToe <- dfToe[,c(1:4,6,5,13,8,14,9,15,16)]
#dat3 <- rbind.data.frame(dat2,dfSDI,dfToe)
#dat3$dts <- as.POSIXct(strptime(dat3$dts, format = "%Y-%m-%d %H:%M:%S"))
#colnames(dat3)[1:2] <- c("Station.Code","datetimestamp")


#dat3 <- dat3[which(dat3$datetimestamp >= as.POSIXct(strptime("2019-01-01 00:00",format = "%Y-%m-%d %H:%M")) & dat3$datetimestamp <= as.POSIXct(strptime("2020-12-31 23:45",format = "%Y-%m-%d %H:%M"))),]

#baddpT <- dat3[which(dat3$SPC < 150 & dat3$Station.Code =="Decker Pool"),]
#dat3 <- dat3[-which(dat3$SPC < 150 & dat3$Station.Code =="Decker Pool"),] ###DMC210721: I added this line because values less than 150 meant that the sonde was not measuring within the water column

#badWP <- dat3[which(dat3$WiperPos < 1.1 | dat3$WiperPos > 1.3),]
#dat3 <- dat3[-which(dat3$WiperPos < 1.1 | dat3$WiperPos > 1.3),]

dat3 <- swmpr(dat3, meta_in = FALSE)
attr(dat3,'timezone')<-"UTC"

agg_dat_sub <- aggreswmp(dat3, by = 'hours', 
                         params = c('Station.Code','TempC','SPC','Turb','DOmgL','ChlRFU','fDOMRFU','fdomConc','PCRFU'), aggs_out = T)
  #params = c('Station.Code','TempC','SPC','Turb','DOmgL','ChlRFU','Chlconc','fDOMRFU','fDOMconc','PCRFU'), aggs_out = T)

summH <- ddply(agg_dat_sub, c("Station.Code","datetimestamp"), summarise,
               Tempbar = mean(TempC),
               SPCbar = mean(SPC),
               Turbbar = mean(Turb),
               DObar = mean(DOmgL),
               ChlRFUbar = mean(ChlRFU),
               #Chlconcbar = mean(Chlconc),
               fDOMRFUbar = mean(fDOMRFU),
               fDOMconcbar = mean(fdomConc),
               PCbar = mean(PCRFU)
               )
agg_dat_sub <- summH

to_plo_sub <- melt(agg_dat_sub, id.var = c('Station.Code','datetimestamp'))
to_plo_sub$dts <- as.POSIXct(strptime(as.character(to_plo_sub$datetimestamp),format = "%Y-%m-%d"))
to_plo_sub$Station.Code <- factor(to_plo_sub$Station.Code, levels = c("Decker Breach","Decker Pool","SDI_USGS","Yolo Flyway Farm","TOE_USGS","LIB_USGS"))#,
                                  #labels = c("P","B","S","Y","T"))
to_plo_sub <- to_plo_sub[which(is.na(to_plo_sub$datetimestamp)==FALSE),]

to_plo_sub$ord <- as.numeric(to_plo_sub$Station.Code)
to_plo_sub <- to_plo_sub[order(to_plo_sub$ord),]

unique(to_plo_sub$Station.Code)
yolo <- c("Yolo Flyway Farm","TOE_USGS","LIB_USGS")
decker <- c("Decker Breach","Decker Pool","SDI_USGS")

xdtsDeck <- to_plo_sub$datetimestamp[which(to_plo_sub$Station.Code == "Decker Breach")]
xdtsYolo <- to_plo_sub$datetimestamp[which(to_plo_sub$Station.Code == "Yolo Flyway Farm")]
xdtsYolo2 <- range(xdtsYolo)
#xdtsYolo2[1]  <- as.POSIXct(strptime("2022-01-01 20:00", format = "%Y-%m-%d %H:%M"),tz = "UTC")

#mycol <- (viridis_pal(option = "H")(9))[c(2,5,8)]
#mysh <- c(24,4,16)

mycol <- (viridis_pal(option = "H")(56))[c(44,24,33)]
mysh <- c(21,25,21)
myps <- c(1,1.5,1)

plo_agg_subT <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% yolo & to_plo_sub$datetimestamp %in% xdtsYolo & to_plo_sub$variable == "Tempbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.7, colour = "black") +#, shape = 21
  #geom_hline(yintercept=25.4) + ###DMC: "Swanson C, Reid T, Young PS, Cech Jr JJ. 2000. Comparative environmental tolerances of threatened delta smelt (Hypomesus transpacificus) and introduced Wakasagi (H. nipponensis) in an altered California estuary. Oecologia 123(3):384-390
  #geom_hline(yintercept=24, linetype="dashed") + ###DMC: reference is "Rich A.A. (1987). Report on studies conducted by Sacramento County to determine the temperatures which optimize growth and survival in juvenile chinook salmon (Onchorhynchus tshawwytscha). McDonough, Holland, & Allen, Sacramento, CA"
  scale_fill_manual(values = mycol,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_shape_manual(values = mysh,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_size_manual(values = myps,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  #theme(axis.text.x = element_text(size = 24)) +
  #theme(axis.text=element_text(size=24)) #+
  #theme(strip.background = element_blank(),strip.text.y = element_blank(),strip.text = element_blank())#+
  xlab("Date") +
  ylab("Temperature (\u00b0C)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())#, axis.title=element_text(size=30,face="bold"), legend.title = element_text(size = 30), legend.text = element_text(size = 24))#+
  #geom_label(data = boxvals, aes(x = factor(datetimestamp), y = 30,label = paste("Mean: ", round(sal, 1), "\nMedian: ", boxmedian.sal, "\nSD: ", round(boxsd.sal,1))), size = 5)

### shape for breach is 4, shape for pool is 24, use circle 20 for channel

plo_agg_subDO <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% yolo & to_plo_sub$datetimestamp %in% xdtsYolo & to_plo_sub$variable == "DObar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.7, colour = "black") +#, shape = 21
  scale_fill_manual(values = mycol,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_shape_manual(values = mysh,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_size_manual(values = myps,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  #scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  #theme(axis.text.x = element_text(size = 24)) +
  #theme(axis.text=element_text(size=24)) #+
  #theme(strip.background = element_blank(),strip.text.y = element_blank(),strip.text = element_blank())#+
  xlab("Date") +
  ylab("Dissolved Oxygen (mg/L)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

plo_agg_subSPC <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% yolo & to_plo_sub$datetimestamp %in% xdtsYolo & to_plo_sub$variable == "SPCbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.7, colour = "black") +
  #geom_hline(yintercept=2.5) + 
  #geom_hline(yintercept=4.6, linetype="dashed") + 
  scale_fill_manual(values = mycol,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_shape_manual(values = mysh,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_size_manual(values = myps,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  #ylim(150,650)+
  theme_classic() +
  xlab("Date") +
  ylab("Specific Conductivity (\u00B5S/cm)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


plo_agg_subTu <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% yolo & to_plo_sub$datetimestamp %in% xdtsYolo & to_plo_sub$variable == "Turbbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.7, colour = "black") +#, shape = 21
  geom_hline(yintercept=12, linetype = "dashed")+
  geom_hline(yintercept=80) +
  scale_fill_manual(values = mycol,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_shape_manual(values = mysh,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_size_manual(values = myps,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  #scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  #theme(axis.text.x = element_text(size = 24)) +
  #theme(axis.text=element_text(size=24)) #+
  #theme(strip.background = element_blank(),strip.text.y = element_blank(),strip.text = element_blank())#+
  xlab("Date") +
  ylab("Turbidity (FNU)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


plo_agg_subChl <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% yolo & to_plo_sub$datetimestamp %in% xdtsYolo & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_shape_manual(values = mysh,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  scale_size_manual(values = myps,labels = c("Flyway","Toe Drain","Liberty\nIsland")) +
  theme_classic() +
  xlab("Date") +
  ylab("Chlorophyll a (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

yoloOnly <- yolo[1]
plo_agg_subChl <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% yoloOnly & to_plo_sub$datetimestamp >= xdtsYolo2[1] & to_plo_sub$datetimestamp <= xdtsYolo2[2] & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[1],labels = c("Flyway   "))+ 
  scale_shape_manual(values = mysh[1],labels = c("Flyway   ")) +
  scale_size_manual(values = myps[1],labels = c("Flyway   ")) +
  theme_classic() +
  xlab("Date") +
  ylab("Chlorophyll a (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


toed <- yolo[2]
plo_agg_subChlToe <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% toed & to_plo_sub$datetimestamp %in% xdtsYolo & to_plo_sub$variable == "Chlconcbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[2],labels = c("Toe Drain"))+ 
  scale_shape_manual(values = mysh[2],labels = c("Toe Drain")) +
  scale_size_manual(values = myps[2],labels = c("Toe Drain")) +
  theme_classic() +
  xlab("Date") +
  ylab("Chlorophyll a (\u00B5g/L)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

gridExtra::grid.arrange(arrangeGrob(plo_agg_subChl, plo_agg_subChlToe,nrow = 2), ncol =1)


yoloOnly <- yolo[1]
plo_agg_subfdom <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% yoloOnly & to_plo_sub$datetimestamp %in% xdtsYolo & to_plo_sub$variable == "fDOMRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[1],labels = c("Flyway   "))+ 
  scale_shape_manual(values = mysh[1],labels = c("Flyway   ")) +
  scale_size_manual(values = myps[1],labels = c("Flyway   ")) +
  theme_classic() +
  #ylim(8,20)+
  xlab("Date") +
  ylab("Fluorescent Dissolved\nOrganic Matter (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


toed <- yolo[2:3]
plo_agg_subfdomtoe <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% toed & to_plo_sub$datetimestamp %in% xdtsYolo & to_plo_sub$variable == "fDOMconcbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[2:3],labels = c("Toe Drain","Liberty\nIsland"))+ 
  scale_shape_manual(values = mysh[2:3],labels = c("Toe Drain","Liberty\nIsland")) +
  scale_size_manual(values = myps[2:3],labels = c("Toe Drain","Liberty\nIsland")) +
  theme_classic() +
  xlab("Date") +
  ylab("Fluorescent Dissolved\nOrganic Matter (mg/L as QSE)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

gridExtra::grid.arrange(arrangeGrob(plo_agg_subfdom, plo_agg_subfdomtoe,nrow = 2), ncol =1)

```


```{r}
for(i in 1:length(wings_stat$avg)){
  if((wings_stat$avg[i] - wings_stat$se[i]) > 0){
    wings_stat$se2[i] = wings_stat$se[i]
  }
  else{
    wings_stat$se2[i] = wings_stat$avg[i]
  }
}




labpos <- c(rep(NA,length(df$col)))
for(i in 1:length(df$col)){
  if(df$season[i] == "Spring"){
    df$labpos[i] = df$avg[i] + df$se[i] + 1000
  }
  if(df$season[i] == "Spring"){
    df$labpos[i] = df$avg[i] + df$se[i] + 1000
  }
  if(df$season[i] == "Spring"){
    df$labpos[i] = df$avg[i] + df$se[i] + 1000
  }
}

season <- c("Winter")
avg <- c("11000")
site <- c("Decker")

dfblank <- data.frame(season,avg,site)

geom_blank(data = dfblank, aes(x = site, y = avg))
library(ggplot2)

ymaxdf <- ddply(df, c("season","site"), summarise,
               ymax = max(avg+se)
               )
df$ymax <- c(rep(NA,length(df$site)))
for(i in 1:length(df$site)){
  for(j in 1:length(ymaxdf$site)){
    if(df$site[i] == ymaxdf$site[j] & df$season[i] == ymaxdf$season[j]){
      df$ymax[i] = ymaxdf$ymax[j]
    }
  }
}
```



This chunk replicates Decker but includes depth
```{r}
library(SWMPr)
library(ggplot2)
library(reshape2)
library(viridis)
library(plyr)
library(scales)
library(gridExtra)

rm(list = ls())
load("BryteChl4LTWQM.RData")
load("FRP_LTMsonde.RData")
#load("ToeDrain_LTMsonde.RData")
#load("SDI_LTMsonde.RData")
dfChlDeck2 <- dfChlDeck[which(dfChlDeck$yr >= 2019 & dfChlDeck$Location2 == "Decker"),]
dfChlDeck2$date <- as.POSIXct(strptime(dfChlDeck2$date, format = "%Y-%m-%d"))#, tz = "America/Los_Angeles")
dfChlDeck2$week <- format(dfChlDeck2$date, "%W")

dat2plo_Start <- as.POSIXct(strptime(c("2019-03-15 00:00","2019-05-15 00:00","2019-09-10 00:00","2019-11-18 00:00","2020-03-01 00:00","2020-06-01 00:00","2020-10-01 00:00"), format = "%Y-%m-%d %H:%M"))
dat2plo_End <- as.POSIXct(strptime(c("2019-04-15 00:00","2019-06-15 00:00","2019-10-10 00:00","2019-12-18 00:00","2020-03-31 00:00","2020-06-30 00:00","2020-10-31 00:00"), format = "%Y-%m-%d %H:%M"))
dateDeck <- data.frame(dat2plo_Start,dat2plo_End)

dat2plo_Actual <- as.POSIXct(strptime(unique(dfChlDeck2$date), format = "%Y-%m-%d"))#, tz = "America/Los_Angeles")
dat2plo_plus3 <- dat2plo_Actual + 3*24*60*60
dat2plo_minus3 <- dat2plo_Actual - 3*24*60*60
dateDeck2 <- data.frame(dat2plo_Actual,dat2plo_minus3, dat2plo_plus3)

dat <- df ### DMC: need to figure out the 8 observations that do not have appropriate datetimestamp #ddd <- df[which(is.na(df$dts == TRUE)),]
dat2 <- dat[,c(5,16,14,11,10,13,6,17,8,18,12,15,7)]
#dat2 <- dat2[,c(1:5,9)]
#colnames(dat2)[5:6] <- c("Turb","DOmgL")
#dfSDI <- dfSDI[,c(1:4,6,5,12,8,13,9,14,15)]
#dfToe <- dfToe[,c(1:4,6,5,13,8,14,9,15,16)]
dat3 <- rbind.data.frame(dat2)#,dfSDI,dfToe)
colnames(dat3)[1:2] <- c("Station.Code","datetimestamp")

dat3 <- dat3[which(dat3$datetimestamp >= as.POSIXct(strptime("2019-01-01 00:00",format = "%Y-%m-%d %H:%M")) & dat3$datetimestamp <= as.POSIXct(strptime("2020-12-31 23:45",format = "%Y-%m-%d %H:%M"))),]

baddpT <- dat3[which(dat3$SPC < 150 & dat3$Station.Code =="Decker Pool"),]
dat3 <- dat3[-which(dat3$SPC < 150 & dat3$Station.Code =="Decker Pool"),] ###DMC210721: I added this line because values less than 150 meant that the sonde was not measuring within the water column

badWP <- dat3[which(dat3$WiperPos < 1.1 | dat3$WiperPos > 1.3),]
dat3 <- dat3[-which(dat3$WiperPos < 1.1 | dat3$WiperPos > 1.3),]

dat3 <- swmpr(dat3, meta_in = FALSE)
attr(dat3,'timezone')<-"UTC"

agg_dat_sub <- aggreswmp(dat3, by = 'hours', 
  params = c('Station.Code','TempC','SPC','Turb','DOmgL','ChlRFU','Chlconc','fDOMRFU','fDOMconc','PCRFU','Depthm'), aggs_out = T)

summH <- ddply(agg_dat_sub, c("Station.Code","datetimestamp"), summarise,
               Tempbar = mean(TempC),
               SPCbar = mean(SPC),
               Turbbar = mean(Turb),
               DObar = mean(DOmgL),
               ChlRFUbar = mean(ChlRFU),
               Chlconcbar = mean(Chlconc),
               fDOMRFUbar = mean(fDOMRFU),
               fDOMconcbar = mean(fDOMconc),
               PCbar = mean(PCRFU),
               Depthbar = mean(Depthm)
               )
agg_dat_sub <- summH

to_plo_sub <- melt(agg_dat_sub, id.var = c('Station.Code','datetimestamp'))
to_plo_sub$dts <- as.POSIXct(strptime(as.character(to_plo_sub$datetimestamp),format = "%Y-%m-%d"))
to_plo_sub$Station.Code <- factor(to_plo_sub$Station.Code, levels = c("Decker Breach","Decker Pool","SacDecker","Yolo Flyway Farm","Toe Drain"))#,
                                  #labels = c("P","B","S","Y","T"))

to_plo_sub$ord <- as.numeric(to_plo_sub$Station.Code)
to_plo_sub <- to_plo_sub[order(to_plo_sub$ord),]

unique(to_plo_sub$Station.Code)
yolo <- c("Yolo Flyway Farm","Toe Drain")
decker <- c("Decker Breach","Decker Pool","SacDecker")

xdtsDeck <- to_plo_sub$datetimestamp[which(to_plo_sub$Station.Code == "Decker Breach")]
xdtsDeck2 <- range(xdtsDeck)
xdtsDeck2[2] <- as.POSIXct(strptime("2020-04-21 20:00", format = "%Y-%m-%d %H:%M"),tz = "UTC")
xdtsYolo <- to_plo_sub$datetimestamp[which(to_plo_sub$Station.Code == "Yolo Flyway Farm")]

mycol <- (viridis_pal(option = "H")(56))[c(24,44,33)]
mycol[3] <- c("black")
mysh <- c(25,21,21)
myps <- c(1.5,1.3,1)
myalf <- c(0.5,0.5,0.7)


plo_agg_subT <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% decker & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "Tempbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +#, shape = 21
  #geom_hline(yintercept=25.4) + ###DMC: "Swanson C, Reid T, Young PS, Cech Jr JJ. 2000. Comparative environmental tolerances of threatened delta smelt (Hypomesus transpacificus) and introduced Wakasagi (H. nipponensis) in an altered California estuary. Oecologia 123(3):384-390
  #geom_hline(yintercept=24, linetype="dashed") + ###DMC: reference is "Rich A.A. (1987). Report on studies conducted by Sacramento County to determine the temperatures which optimize growth and survival in juvenile chinook salmon (Onchorhynchus tshawwytscha). McDonough, Holland, & Allen, Sacramento, CA"
  scale_fill_manual(values = mycol,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_shape_manual(values = mysh,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_size_manual(values = myps,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior","Sacramento\nRiver")) +
  theme_classic() +
  xlab("Date") +
  ylab("Temperature (\u00b0C)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


plo_agg_subDO <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% decker & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "DObar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code,shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +
  #geom_hline(yintercept=2.5) + 
  #geom_hline(yintercept=4.6, linetype="dashed") + 
  scale_fill_manual(values = mycol,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_shape_manual(values = mysh,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_size_manual(values = myps,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior","Sacramento\nRiver")) +
  theme_classic() +
  xlab("Date") +
  ylab("Dissolved Oxygen (mg/L)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

plo_agg_subSPC <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% decker & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "SPCbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +
  #geom_hline(yintercept=2.5) + 
  #geom_hline(yintercept=4.6, linetype="dashed") + 
  scale_fill_manual(values = mycol,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_shape_manual(values = mysh,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_size_manual(values = myps,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior","Sacramento\nRiver")) +
  ylim(150,650)+
  theme_classic() +
  xlab("Date") +
  ylab("Specific Conductivity (\u00B5S/cm)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
pl2 <- plo_agg_subSPC + annotation_custom(grob = ggplotGrob(plo_agg_subSPC +ylim(0,2100) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         xmin = as.POSIXct(strptime("2020-01-05",format = "%Y-%m-%d")),
                                         #xmax = as.POSIXct(strptime("2020-01-01",format = "%Y-%m-%d")), 
                                         ymin = 375, ymax = 675)


plo_agg_subTu <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% decker & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "Turbbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +
  geom_hline(yintercept=12, linetype = "dashed")+ #Grimaldo LF, Sommer T, Van Ark N, Jones G, Holland E, Moyle PB, Smith P, Herbold B. 2009a. Factors affecting fish entrainment into massive water diversions in a freshwater tidal estuary: Can fish losses be managed? N Am J Fish Manage 29:1253-1270.
  geom_hline(yintercept=80) + # Can also use this for the above '12' turbidity value too: Hasenbein M, Fangue NA, Geist J, Komoroske LM, Truong J, McPherson R, Connon RE (2016) Assessments at multiple levels of biological organization allow for an integrative determination of physiological tolerances to turbidity in an endangered fish species. Conserv Physiol 4: doi:10.1093/conphys/cow004.
  scale_fill_manual(values = mycol,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_shape_manual(values = mysh,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_size_manual(values = myps,labels = c("Breach","Interior","Sacramento\nRiver")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior","Sacramento\nRiver")) +
  ylim(0,400)+
  theme_classic() +
  xlab("Date") +
  ylab("Turbidity (FNU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

pl2 <- plo_agg_subTu + annotation_custom(grob = ggplotGrob(plo_agg_subTu +ylim(0,NA) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         #xmin = as.POSIXct(strptime("2020-01-10",format = "%Y-%m-%d")),
                                         xmax = as.POSIXct(strptime("2020-03-15",format = "%Y-%m-%d")), 
                                         ymin = 200, ymax = 425)

###DMC210723: pick up here... wiper was down for Decker Breach prior to 200107 ###DMC210727: omitted the data for Decker Breach prior to 20
deckerOnly <- decker[1:2]
#plo_agg_subChl <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
plo_agg_subChl <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(colour = "black") +
  geom_line(data = to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & to_plo_sub$variable == "Depthbar"),], aes(x = datetimestamp, y = value*2.5, colour = Station.Code),size = 0.5) +
  scale_colour_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
  scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior")) +
  theme_classic() +
  ylim(0,5) +
  xlab("Date") +
  ylab("Chlorophyll a (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
pl2 <- plo_agg_subChl + annotation_custom(grob = ggplotGrob(plo_agg_subChl +ylim(0,175) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         xmin = as.POSIXct(strptime("2020-01-10",format = "%Y-%m-%d")),
                                         #xmax = as.POSIXct(strptime("2020-01-01",format = "%Y-%m-%d")), 
                                         ymin = 1.5, ymax = 5.2)

x <- seq(0,100)
y <- seq(0,400,by=4)
dfCHLRFU <- data.frame(x,y)
plot(x,y)

deckerOnly <- decker[1:2]
dateDeck <- dateDeck[-1,]
listDeck <- list()
for(i in 1:nrow(dateDeck)){
  df <- to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly  & to_plo_sub$datetimestamp > dateDeck$dat2plo_Start[i] & to_plo_sub$datetimestamp < dateDeck$dat2plo_End[i]),]
  #maxDbreach <- max(df$value[which(df$variable == "Depthbar" & df$Station.Code == "Decker Breach")])
  plo_agg_subChl <- ggplot(df[which(df$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, colour = Station.Code, shape = Station.Code, size = Station.Code)) +
    
    geom_line(data = df[which(df$Station.Code %in% deckerOnly & df$variable == "Depthbar"),], aes(x = datetimestamp, y = value),size = 0.5, colour = "gray") +
    geom_line(size = 0.5) +
    scale_colour_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
    scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
    scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
    scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
    scale_alpha_manual(values = myalf,labels = c("Breach","Interior")) +
    theme_classic() +
    #ylim(0,5) +
    xlab("Date") +
    ylab("Chlorophyll a (RFU)") +
    theme(axis.text.x =element_text(),
          axis.title = element_text(face = "bold"),
          legend.title = element_blank())
  listDeck[[i]] <- plo_agg_subChl
}
listDeck[[3]]


deckerOnly <- decker[1:2]
listDeck <- list()
for(i in 1:nrow(dateDeck2)){
  df <- to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly  & to_plo_sub$datetimestamp > dateDeck2$dat2plo_minus3[i] & to_plo_sub$datetimestamp < dateDeck2$dat2plo_plus3[i]),]
  #maxDbreach <- max(df$value[which(df$variable == "Depthbar" & df$Station.Code == "Decker Breach")])
  plo_agg_subChl <- ggplot(df[which(df$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, colour = Station.Code, shape = Station.Code, size = Station.Code)) +
    
    geom_line(data = df[which(df$Station.Code %in% deckerOnly & df$variable == "Depthbar"),], aes(x = datetimestamp, y = value),size = 0.5, colour = "gray") +
    geom_vline(xintercept = dateDeck2$dat2plo_Actual[i]) +
    geom_line(size = 0.5) +
    scale_colour_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
    scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
    scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
    scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
    scale_alpha_manual(values = myalf,labels = c("Breach","Interior")) +
    theme_classic() +
    #ylim(0,5) +
    xlab("Date") +
    ylab("Chlorophyll a (RFU)") +
    theme(axis.text.x =element_text(),
          axis.title = element_text(face = "bold"),
          legend.title = element_blank())
  listDeck[[i]] <- plo_agg_subChl
}
listDeck[[3]]

sac <- decker[3]
plo_agg_subChlsac <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% sac & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "Chlconcbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[3],labels = c("Sac.\nRiver   "))+ 
  scale_shape_manual(values = mysh[3],labels = c("Sac.\nRiver   ")) +
  scale_size_manual(values = myps[3],labels = c("Sac.\nRiver   ")) +
  theme_classic() +
  xlab("Date") +
  ylab("Chlorophyll a (\u00B5g/L)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

gridExtra::grid.arrange(arrangeGrob(pl2, plo_agg_subChlsac,nrow = 2), ncol =1)


plo_agg_subChlBoth <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "ChlRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, alpha = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(data = to_plo_sub[which(to_plo_sub$Station.Code %in% sac & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "Chlconcbar"),], aes(x = datetimestamp, y = value-1), fill = mycol[3], shape = mysh[3], size = myps[3]) +
  geom_point(colour = "black") +
  scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
  scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
  scale_alpha_manual(values = myalf,labels = c("Breach","Interior")) +
  scale_y_continuous(sec.axis = sec_axis(~.-1, name = "Chlorophyll a (\u00B5g/L)"))+
  theme_classic() +
  ylim(0,5) +
  xlab("Date") +
  ylab("Chlorophyll a (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
pl2 <- plo_agg_subChl + annotation_custom(grob = ggplotGrob(plo_agg_subChl +ylim(0,175) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         xmin = as.POSIXct(strptime("2020-01-10",format = "%Y-%m-%d")),
                                         #xmax = as.POSIXct(strptime("2020-01-01",format = "%Y-%m-%d")), 
                                         ymin = 1.5, ymax = 5.2)



deckerOnly <- decker[1:2]
plo_agg_subPC <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "PCbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  #geom_hline(yintercept=12, linetype = "dashed")+ #Grimaldo LF, Sommer T, Van Ark N, Jones G, Holland E, Moyle PB, Smith P, Herbold B. 2009a. Factors affecting fish entrainment into massive water diversions in a freshwater tidal estuary: Can fish losses be managed? N Am J Fish Manage 29:1253-1270.
  #geom_hline(yintercept=80) + # Can also use this for the above '12' turbidity value too: Hasenbein M, Fangue NA, Geist J, Komoroske LM, Truong J, McPherson R, Connon RE (2016) Assessments at multiple levels of biological organization allow for an integrative determination of physiological tolerances to turbidity in an endangered fish species. Conserv Physiol 4: doi:10.1093/conphys/cow004.
  scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
  scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
  #scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  ylim(0,5) +
  #theme(axis.text.x = element_text(size = 24)) +
  #theme(axis.text=element_text(size=24)) #+
  #theme(strip.background = element_blank(),strip.text.y = element_blank(),strip.text = element_blank())#+
  xlab("Date") +
  ylab("Phycocyanin (RFU)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())
pl2 <- plo_agg_subPC + annotation_custom(grob = ggplotGrob(plo_agg_subPC +ylim(0,NA) + 
                                                             theme(axis.title = element_blank(),
                                                                   legend.position = "none")),
                                         #xmin = as.POSIXct(strptime("2020-01-10",format = "%Y-%m-%d")),
                                         xmax = as.POSIXct(strptime("2020-03-15",format = "%Y-%m-%d")), 
                                         ymin = 1.7, ymax = 5.2)

deckerOnly <- decker[1:2]
plo_agg_subfdom <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% deckerOnly & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "fDOMRFUbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[1:2],labels = c("Breach","Interior"))+ 
  scale_shape_manual(values = mysh[1:2],labels = c("Breach","Interior")) +
  scale_size_manual(values = myps[1:2],labels = c("Breach","Interior")) +
  theme_classic() +
  #ylim(0,5) +
  xlab("Date") +
  ylab("Fluorescent Dissolved\nOrganic Matter (RFU)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


sac <- decker[3]
plo_agg_subfdomsac <- ggplot(to_plo_sub[which(to_plo_sub$Station.Code %in% sac & (to_plo_sub$datetimestamp >= xdtsDeck2[1] & to_plo_sub$datetimestamp <= xdtsDeck2[2]) & to_plo_sub$variable == "fDOMconcbar"),], aes(x = datetimestamp, y = value, fill = Station.Code, shape = Station.Code, size = Station.Code)) +
  geom_point(alpha = 0.5, colour = "black") +
  scale_fill_manual(values = mycol[3],labels = c("Sac.\nRiver   "))+ 
  scale_shape_manual(values = mysh[3],labels = c("Sac.\nRiver   ")) +
  scale_size_manual(values = myps[3],labels = c("Sac.\nRiver   ")) +
  theme_classic() +
  xlab("Date") +
  ylab("Fluorescent Dissolved\nOrganic Matter (mg/L as QSE)") +
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())


gridExtra::grid.arrange(arrangeGrob(plo_agg_subfdom, plo_agg_subfdomsac,nrow = 2), ncol =1)

sites <- c(yolo, decker)
p <- list()
for(i in seq_along(sites)){
  df <- agg_dat_subD[which(agg_dat_subD$Station.Code == sites[i]),]
  dfT95 <- aggregate(TempC ~ datetimestamp, data = df, FUN = quantile, probs  = 0.95)
  dfT95$qua <- c("pct95")
  dfT95$lt <- c("dotted")
  dfT50 <- aggregate(TempC ~ datetimestamp, data = df, FUN = quantile, probs  = 0.50)
  dfT50$qua <- c("median")
  dfT50$lt <- c("solid")
  dfT05 <- aggregate(TempC ~ datetimestamp, data = df, FUN = quantile, probs  = 0.05)
  dfT05$qua <- c("pct5")
  dfT05$lt <- c("dashed")
  dfD95 <- aggregate(DOmgL ~ datetimestamp, data = df, FUN = quantile, probs  = 0.95)
  dfD95$qua <- c("pct95")
  dfD95$lt <- c("dotted")
  dfD50 <- aggregate(DOmgL ~ datetimestamp, data = df, FUN = quantile, probs  = 0.50)
  dfD50$qua <- c("median")
  dfD50$lt <- c("solid")
  dfD05 <- aggregate(DOmgL ~ datetimestamp, data = df, FUN = quantile, probs  = 0.05)
  dfD05$qua <- c("pct5")
  dfD05$lt <- c("dashed")
  dfTu95 <- aggregate(Turb ~ datetimestamp, data = df, FUN = quantile, probs  = 0.95)
  dfTu95$qua <- c("pct95")
  dfTu95$lt <- c("dotted")
  dfTu50 <- aggregate(Turb ~ datetimestamp, data = df, FUN = quantile, probs  = 0.50)
  dfTu50$qua <- c("median")
  dfTu50$lt <- c("solid")
  dfTu05 <- aggregate(Turb ~ datetimestamp, data = df, FUN = quantile, probs  = 0.05)
  dfTu05$qua <- c("pct5")
  dfTu05$lt <- c("dashed")
  dfT <- rbind.data.frame(dfT95,dfT50,dfT05)
  dfT$variable <- "TempC"
  colnames(dfT)[2] <- c("value")
  dfT$Site <- sites[i]
  dfD <- rbind.data.frame(dfD95,dfD50,dfD05)
  dfD$variable <- "DOmgL"
  dfD$Site <- sites[i]
  colnames(dfD)[2] <- c("value")
  dfTu <- rbind.data.frame(dfTu95,dfTu50,dfTu05)
  dfTu$variable <- "Turb"
  colnames(dfTu)[2] <- c("value")
  dfTu$Site <- sites[i]
  p[[i]] <- rbind.data.frame(dfT,dfD,dfTu)
}
names(p) <- sites
to_plo2 <- do.call(rbind.data.frame, p)

xdtsDeck2 <- to_plo2$datetimestamp[which(to_plo2$Site == "Decker Breach")]
xdtsYolo2 <- to_plo2$datetimestamp[which(to_plo2$Site == "Yolo Flyway Farm")]

plo_stat <- ggplot(to_plo2[which(to_plo2$Site %in% yolo & to_plo2$datetimestamp %in% xdtsYolo2),], aes(x = datetimestamp, y = value, colour = Site, linetype = lt)) +
  geom_line() +
  facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() 



to_plo3 <- dcast(to_plo2,datetimestamp+Site+variable ~qua)
to_plo3$variable <- factor(to_plo3$variable, levels = c("TempC","DOmgL","Turb"), labels = c("Temperature (C)","Dissolved Oxygen (mg/L)","Turbidity (FNU)"))
plo_stat2 <- ggplot(to_plo3[which(to_plo3$Site %in% decker & to_plo3$datetimestamp %in% xdtsDeck2),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  theme(axis.title.y = element_blank())

plo_stat2 <- ggplot(to_plo3[which(to_plo3$Site %in% yolo & to_plo3$datetimestamp %in% xdtsYolo2),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  theme(axis.title.y = element_blank())


### Feb21 to Mar16 had no sondes
skipS <- c(as.POSIXct(strptime(c('2020-02-21 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-12 04:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-21 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-12 04:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-21 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-12 04:00:00'),format = "%Y-%m-%d %H:%M")))
skipE <- c(as.POSIXct(strptime(c('2020-03-18 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-13 16:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-03-18 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-13 16:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-03-18 00:00:00'),format = "%Y-%m-%d %H:%M")),
           as.POSIXct(strptime(c('2020-02-13 16:00:00'),format = "%Y-%m-%d %H:%M")))
valmax <- c(23,23,12,12,400,400)#max(to_plo3$pct95[which(to_plo3$variable== "Temperature (C)")])
valmin <- c(5,5,5,5,0,0)#min(to_plo3$pct5[which(to_plo3$variable== "Temperature (C)")])
varSkip <- c("temp","temp","do","do","turb","turb")
dfBox <- data.frame(skipS,skipE,valmax,valmin, varSkip)

plo_stat4 <- ggplot(to_plo3[which(to_plo3$Site %in% decker & to_plo3$datetimestamp %in% xdtsDeck2 & to_plo3$variable=="Temperature (C)"),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  geom_hline(yintercept=25.4) + 
  geom_hline(yintercept=24, linetype="dashed") + 
  geom_rect(data = dfBox[which(dfBox$varSkip == "temp"),], aes(xmin = skipS, xmax = skipE, ymin = valmin, ymax = valmax),color = "white",fill="white")+
  scale_color_manual(values = mycol,labels = c("Pool","Breach","Channel")) +
  #scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  xlab("Date") +
  ylab("Temperature (C)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

plo_stat5 <- ggplot(to_plo3[which(to_plo3$Site %in% decker & to_plo3$datetimestamp %in% xdtsDeck2 & to_plo3$variable=="Dissolved Oxygen (mg/L)"),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  geom_hline(yintercept=2.5) + 
  geom_hline(yintercept=4.6, linetype="dashed") + 
  geom_rect(data = dfBox[which(dfBox$varSkip == "do"),], aes(xmin = skipS, xmax = skipE, ymin = valmin, ymax = valmax),color = "white",fill="white")+
  scale_color_manual(values = mycol,labels = c("Pool","Breach","Channel")) +
  scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  xlab("Date") +
  ylab("Dissolved Oxygen (mg/L)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

plo_stat6 <- ggplot(to_plo3[which(to_plo3$Site %in% decker & to_plo3$datetimestamp %in% xdtsDeck2 & to_plo3$variable=="Turbidity (FNU)"),], aes(colour = Site)) +
  geom_line(aes(x = datetimestamp, y = median), linetype = c("dashed")) +
  geom_ribbon(aes(ymin = pct5, ymax = pct95, fill = Site,x = datetimestamp),alpha = 0.3) +
  geom_rect(data = dfBox[which(dfBox$varSkip == "turb"),], aes(xmin = skipS, xmax = skipE, ymin = valmin, ymax = valmax),color = "white",fill="white")+
  geom_hline(yintercept=12)+
  geom_hline(yintercept=80) + 
  scale_color_manual(values = mycol,labels = c("Pool","Breach","Channel")) +
  scale_shape_manual(values = mysh,labels = c("Pool","Breach","Channel")) +
  #facet_wrap(~ variable, ncol = 1, scales = 'free_y') + 
  theme_classic() +
  xlab("Date") +
  ylab("Turbidity (FNU)") +
  #theme(axis.text.x =element_blank())+
  theme(axis.text.x =element_text(),
        axis.title = element_text(face = "bold"),
        legend.title = element_blank())

```
