---
title: "FRP_ContinuousWQ_ErrorCalculations"
author: "DMC"
date: "7/12/2023"
output: html_document
---

The goal of this file is to use exchange worksheets and calibration worksheets to calculate the error due to fouling of sensors and sensor drift.

First, we'll load the Exchange Worksheet and calculate the error associated with fouling
```{r Fouling data}
rm(list = ls())
load(here::here("working","CDFW_ExchangeWorksheet.RData"))

### split up all the variables by sonde and timing of measurements
# pre-cleaning
preclean_recov <- c("preclean_recov_temp","preclean_recov_DO","preclean_recov_sc","preclean_recov_pH","preclean_recov_turb","preclean_recov_pc","preclean_recov_chl","preclean_recov_fdom")
preclean_verif <- c("preclean_verif_temp","preclean_verif_DO","preclean_verif_sc","preclean_verif_pH","preclean_verif_turb","preclean_verif_pc","preclean_verif_chl","preclean_verif_fdom")
# post-cleaning
postclean_recov <- c("postclean_recov_temp","postclean_recov_DO","postclean_recov_sc","postclean_recov_pH","postclean_recov_turb","postclean_recov_pc","postclean_recov_chl","postclean_recov_fdom")
postclean_verif <- c("postclean_verif_temp","postclean_verif_DO","postclean_verif_sc","postclean_verif_pH","postclean_verif_turb","postclean_verif_pc","postclean_verif_chl","postclean_verif_fdom")

# make a list to populate with fouling differences
list_foul <- list()
for(i in 1:nrow(df_Exch)){
  sondeID <- ifelse(df_Exch$recovered_sonde_id[i] == "Other", df_Exch$recovered_sonde_other[i], df_Exch$recovered_sonde_id[i]) # grab sondeID of sonde being recovered
  dateRecov <- df_Exch$date2[i] # grab date of recovery
  station <- df_Exch$station[i] # grab station
  mat_recov_pre <- as.matrix(data.frame(sapply(df_Exch[i,c(preclean_recov)], function(x) as.numeric(as.character(x))))) # make a matrix of pre-clean measurements for recovered sonde
  mat_recov_post <- as.matrix(data.frame(sapply(df_Exch[i,c(postclean_recov)], function(x) as.numeric(as.character(x)))))# make a matrix of post-clean measurements for recovered sonde
  mat_recov_diff <- mat_recov_post - mat_recov_pre # find difference between matrices for recovered sonde
  mat_verif_pre <- as.matrix(data.frame(sapply(df_Exch[i,c(preclean_verif)], function(x) as.numeric(as.character(x)))))# make a matrix of pre-clean measurements for verification sonde
  mat_verif_post <- as.matrix(data.frame(sapply(df_Exch[i,c(postclean_verif)], function(x) as.numeric(as.character(x)))))# make a matrix of post-clean measurements for verification sonde
  mat_verif_diff <- mat_verif_post - mat_verif_pre # find difference between matrices for verification sonde
  mat_foul_num <- mat_recov_diff - mat_verif_diff # find fouling error in raw numerical
  mat_foul_perc <- (mat_foul_num/mat_recov_pre)#*100 # find fouling error in percent -> proportion really
  df_foul_num <- data.frame(mat_foul_num) # make a dataframe of numeric error
  df_foul_num$varX <- substr(rownames(df_foul_num),17, nchar(rownames(df_foul_num))) # make variable to store metrics
  df_foul_perc <- data.frame(mat_foul_perc) # make a dataframe of percent error
  df_foul_perc$varX <- substr(rownames(df_foul_perc),17, nchar(rownames(df_foul_perc))) # make variable to store metrics
  colnames(df_foul_num) <- c("valueX","varX")
  colnames(df_foul_perc) <- c("valueX","varX")
  rownames(df_foul_num) <- NULL
  rownames(df_foul_perc) <- NULL
  list_temp <- list(df_foul_num, df_foul_perc, sondeID, dateRecov, station) # store all fouling calculations and metadata in temporary list
  names(list_temp) <- c("foul_num","foul_perc","sondeID","dateRecov","station")
  list_foul[[i]] <- list_temp # store temporary list in overarching list
  rm(list_temp, mat_recov_pre, mat_recov_post, mat_recov_diff, mat_verif_pre, mat_verif_post, mat_verif_diff, mat_foul_num, mat_foul_perc, df_foul_num, df_foul_perc, sondeID, station, dateRecov)
}
names(list_foul) <- paste(ifelse(df_Exch$recovered_sonde_id == "Other", df_Exch$recovered_sonde_other, df_Exch$recovered_sonde_id),
                          df_Exch$date2, sep = " ") # name list items by sondeID and recovery date

save(list_foul, file = here::here("working","FoulingError.RData"))
```

In this chunk, we'll load the Calibration Worksheet and calculate the error associated with sensor drift
```{r Calibration Data}
rm(list = ls())
load(here::here("working","CDFW_CalibrationWorksheet.RData"))

# make a new standard value for measuring conductivity in air; this will allow for a difference to be calculated in matrix form
df_CalibData$sc_InAir0 <- 0

### split up all the variables by timing of measurements
# grab values for measurements taken before calibration
pre_values <- colnames(df_CalibData)[stringr::str_detect(colnames(df_CalibData), "_pre")]
pre_values <- c(pre_values, "temp_sonde", "sc_InAir")
# grab values for measurements taken after calibration (i.e. concentrations of standards)
post_values <- colnames(df_CalibData)[stringr::str_detect(colnames(df_CalibData), "_post")]
post_values <- post_values[-which(post_values %in% c("pre_post","DO_concentration_post"))]
post_values <- c(post_values, "temp_NIST", "sc_InAir0")

# make a vector of NA for metrics that use DI water as zero-point in calibrations
drift_postVar_NA <- c("fdom_zero","chl_zero","pc_zero","turb_zero")

# make a list to populate with calibration differences
list_drift <- list()
for(i in 1:nrow(df_CalibData)){
  if(df_CalibData$discrete_or_continuous[i] == "Continuous" & df_CalibData$pre_post[i] == "Post"){
    sondeID <- ifelse(df_CalibData$sonde_id[i] == "Other", df_CalibData$sonde_other[i], df_CalibData$sonde_id[i]) # grab sondeID of sonde being recovered
    dateRecov <- as.Date(df_CalibData$dts_startstop[i]) # grab date of recovery
    #station <- df_CalibData$station[i]
    mat_pre <- as.matrix(data.frame(sapply(df_CalibData[i,c(pre_values)], function(x) as.numeric(as.character(x)))))# make a matrix of pre-calibration measurements for recovered sonde
    mat_post <- as.matrix(data.frame(sapply(df_CalibData[i,c(post_values)], function(x) as.numeric(as.character(x)))))# make a matrix of post-calibration measurements for recovered sonde (i.e. concentrations of standards)
    mat_drift_num <- mat_post - mat_pre # find difference between matrices for sensor drift
    mat_drift_perc <- (mat_drift_num/mat_pre)#*100 # find drift error in percent -> proportion really
    df_drift_num <- data.frame(mat_drift_num)# make a dataframe of numeric error
    df_drift_num$varX <- rownames(df_drift_num)# make variable to store metrics
    df_drift_num$varX <- gsub("_post","",df_drift_num$varX, fixed = TRUE)# remove unnecessary part of name
    df_drift_perc <- data.frame(mat_drift_perc)# make a dataframe of percent error
    df_drift_perc$varX <- rownames(df_drift_perc)# make variable to store metrics
    df_drift_perc$varX <- gsub("_post","",df_drift_perc$varX, fixed = TRUE)# remove unnecessary part of name
    colnames(df_drift_num) <- c("valueX","varX")
    colnames(df_drift_perc) <- c("valueX","varX")
    rownames(df_drift_num) <- NULL
    rownames(df_drift_perc) <- NULL
    df_drift_perc$valueX[which(df_drift_perc$varX %in% drift_postVar_NA)] <- NA # force percent values for zero-point calibrations to become NA
    list_temp <- list(df_drift_num, df_drift_perc, sondeID, dateRecov)# store all drift calculations and metadata in temporary list
    names(list_temp) <- c("drift_num","drift_perc","sondeID","dateRecov")
    list_drift[[i]] <- list_temp# store temporary list in overarching list
    rm(list_temp, mat_pre, mat_post, mat_drift_num, mat_drift_perc, df_drift_num, df_drift_perc, sondeID, dateRecov)
  } else {
    list_drift[[i]] <- NULL
  }
}
names(list_drift) <- paste(ifelse(df_CalibData$sonde_id == "Other", df_CalibData$sonde_other, df_CalibData$sonde_id),
                          as.Date(df_CalibData$dts_startstop), sep = " ")# name list items by sondeID and recovery date

save(list_drift, file = here::here("working","DriftError.RData"))
```

This chunk makes tables of criteria to base quality scores (ratings). Based mostly from DWR calculation sheet and the biological sensors critera are from the FRP QAPP
```{r Error ratings}
rm(list = ls())

df_Ratings_num <- data.frame(varX = c("temp","sc","DO","pH","turb","chl","pc","fdom"),
                             zed = c(0),# important for making logical statement further downstream
                         Excellent = c(0.2, 2, 0.3, 0.2, 0.5, 0.125, 0.125, 0.166),
                         Good = c(0.5, 4, 0.5, 0.5, 1, 0.25, 0.5, 0.333),
                         Fair = c(0.8, 6, 0.8, 0.8, 1.5, 0.5, 0.5, 0.666),
                         Poor = c(2, 8, 2, 2, 3, 0.75, 0.75, 1),
                         MaxLimit = c(999))# important for making logical statement further downstream
df_Ratings_perc <- data.frame(varX = c("temp","sc","DO","pH","turb","chl","pc","fdom"),
                              zed = c(NA,0,0,NA,0,0,0,0),# important for making logical statement further downstream
                         Excellent = c(NA, 0.03, 0.05, NA, 0.05, 0.05, 0.05, 0.05),
                         Good = c(NA, 0.1, 0.1, NA, 0.1, 0.1, 0.1, 0.1),
                         Fair = c(NA, 0.15, 0.15, NA, 0.15, 0.15, 0.15, 0.15),
                         Poor = c(NA, 0.3, 0.2, NA, 0.3, 0.2, 0.2, 0.2),
                         MaxLimit = c(NA,999,999,NA,999,999,999,999))# important for making logical statement further downstream

save(df_Ratings_num, df_Ratings_perc, file = here::here("working","ErrorRatings.RData"))
```

This chunk calculates total error from both fouling and sensor drift
```{r Total Error}
rm(list = ls())
load(here::here("working","FoulingError.RData"))
load(here::here("working","DriftError.RData"))
load(here::here("working","ErrorRatings.RData"))

### We need to make a expanded dataframe to establish relationships between fouling and sensor drift values
varDrift <- list_drift[[3]][[1]]$varX[1:12] # grabs the first 12 variables from sensor drift
varFoul <- c("fdom","fdom","chl","chl","pc","pc","turb","turb","sc","pH","pH","pH") # write out matching variable names for fouling datasets
df_Variables <- data.frame(varFoul, varDrift) # create the dataframe

uniqVar <- list_foul[[3]][[1]]$varX # make an object with unique variable names in fouling dataset

# make a list to populate with total error calculations and ratings
list_ratings <- list()
for(i in 1:length(list_foul)){
  for(j in 1:length(list_drift)){
    if(names(list_foul[i]) == names(list_drift)[j]){ # match up the two datasets by common name
      df_TotalError <- data.frame(varX = c("temp","pH","DO","sc","chl","pc","fdom","turb"), # make a dataframe to populate
                                  TotalError_num = NA, 
                                  TotalError_perc = NA,
                                  Rating_num = NA,
                                  Rating_perc = NA)
      for(k in 1:nrow(df_TotalError)){
        varX_Foul <- df_TotalError$varX[k] # variable of interest in fouling dataset
        varX_Drift <- df_Variables$varDrift[which(df_Variables$varFoul == varX_Foul)] # variable of interest in drift dataset
        df_TotalError$TotalError_num[k] <- sum( # add the fouling error plus the error found with calibration standards (average of standards if 2 or more are used)
          abs(list_foul[[i]][["foul_num"]]$valueX[which(list_foul[[i]][["foul_num"]]$varX == varX_Foul)]),
          ifelse(is.na(list_drift[[j]][["drift_num"]]$valueX[which(list_drift[[j]][["drift_num"]]$varX %in% varX_Drift)]),
                 abs(list_drift[[j]][["drift_num"]]$valueX[which(list_drift[[j]][["drift_num"]]$varX %in% varX_Drift[1])]),
                 mean(abs(list_drift[[j]][["drift_num"]]$valueX[which(list_drift[[j]][["drift_num"]]$varX %in% varX_Drift)]),
                      na.rm = TRUE)),
          na.rm = TRUE)
        df_TotalError$TotalError_perc[k] <- sum( # add the fouling error plus the error found with calibration standards (average of standards if 2 or more are used)
          abs(list_foul[[i]][["foul_perc"]]$valueX[which(list_foul[[i]][["foul_perc"]]$varX == varX_Foul)]),
          ifelse(is.na(list_drift[[j]][["drift_perc"]]$valueX[which(list_drift[[j]][["drift_perc"]]$varX %in% varX_Drift)]),
                 abs(list_drift[[j]][["drift_perc"]]$valueX[which(list_drift[[j]][["drift_perc"]]$varX %in% varX_Drift[1])]),
                 mean(abs(list_drift[[j]][["drift_perc"]]$valueX[which(list_drift[[j]][["drift_perc"]]$varX %in% varX_Drift)]),
                      na.rm = TRUE)),
          na.rm = TRUE)
        for(a in 3:ncol(df_Ratings_num)){ # attribute a rating if numerical error or percent error fall within the criteria establish in ratings tables
          if(df_TotalError$TotalError_num[k] > df_Ratings_num[which(df_Ratings_num$varX == varX_Foul),a-1] 
             & df_TotalError$TotalError_num[k] <= df_Ratings_num[which(df_Ratings_num$varX == varX_Foul),a]){
            df_TotalError$Rating_num[k] = colnames(df_Ratings_num)[a]
          }
          tryCatch({ # tryCatch necessary for forcing loop to skip if there is a NA in the percent variable
            if(df_TotalError$TotalError_perc[k] > df_Ratings_perc[which(df_Ratings_perc$varX == varX_Foul),a-1] 
               & df_TotalError$TotalError_perc[k] <= df_Ratings_perc[which(df_Ratings_perc$varX == varX_Foul),a]){
              df_TotalError$Rating_perc[k] = colnames(df_Ratings_perc)[a]
              }
            } , 
            # when an error is encountered, the loop will be forced to continue and the warning(s) will be shown at the end
            error = function(e){ skip_to_next <<- TRUE})
          if(skip_to_next) {next}
        }
        list_ratings[[i]] <- list(df_TotalError)
      }
    }
  }
}
names(list_ratings) <- names(list_foul)


```

