---
title: "ExtProgram_Data"
author: "DMC"
date: "8/1/2024"
output: html_document
---

For 2023 data from USGS Toe Drain station near Yolo Flyway Farms
```{r}
library(tidyverse)
library(dataRetrieval)
rm(list = ls())

siteNumber <- "11455140"
parameterCd <- "00065" # Discharge
startDate <- "2023-01-01T00:00"
endDate <- "2023-12-31T23:45"
timezone <- "America/Los_Angeles"

parameterQ <- read.csv(here::here("raw","ExtPrograms","USGS","USGS_parameters.csv"))

# dailyDataAvailable <- whatNWISdata(
#  siteNumber = siteNumber,
#  service = "iv"
# )
# dailyDataAvailable$parameter <- NA
# dailyDataAvailable2 <- merge(dailyDataAvailable, parameterQ[,c(1,3)], by = "parm_cd")
# siteINFO <- readNWISsite(siteNumber)
# siteAll <- readNWISdata(sites = siteNumber, service = "iv", startDate = startDate, endDate = endDate,tz = timezone)

#save(siteAll, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_11455140.RData"))

load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_11455140.RData"))

col2get <- data.frame(colnames(siteAll),NA)
col2get[,2] <- stringr::str_match(col2get[,1], "_\\d+")
col2get$parm_cd <- substr(col2get[,2],2,nchar(col2get[,2]))
colnames(col2get) <- c("colsNames","num1","parm_cd")
col2get2 <- merge(col2get,parameterQ[,c(1,3)],by = "parm_cd")

df_ToeDrain <- siteAll[,c(2,3,12,13, # 12 and 13 are DO and its QC status
                          which(colnames(siteAll) %in% col2get2[c(1,2, #temperature of upper sonde and its QC status
                                                                    8,7,# SC of upper sonde and its QC status
                                                                    13,14,# fdom of upper sonde and its QC status
                                                                    16,15,# chl of upper sonde and its QC status
                                                                    17,18,# turb of upper sonde and its QC status
                                                                    9,10,# pH and its QC status
                                                                    5,6) # gage height and its QC status
                                                                  ,"colsNames"] 
                                  ))] 

col2get2$parm_nm
colnames(df_ToeDrain)[3:18] <- c("do","do_flag","tempC","tempC_flag","gage","gage_flag","sc","sc_flag","pH","pH_flag","fdom","fdom_flag","chl","chl_flag","turb","turb_flag")

save(df_ToeDrain, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_ToeDrain.RData"))
```

For 2023 data from USGS Liberty Island station near Yolo Flyway Farms
```{r}
library(tidyverse)
library(dataRetrieval)
rm(list = ls())

siteNumber <- "11455315"
parameterCd <- "00065" # Discharge
startDate <- "2023-01-01T00:00"
endDate <- "2023-12-31T23:45"
timezone <- "America/Los_Angeles"

parameterQ <- read.csv(here::here("raw","ExtPrograms","USGS","USGS_parameters.csv"))

# dailyDataAvailable <- whatNWISdata(
#  siteNumber = siteNumber,
#  service = "iv"
# )
# dailyDataAvailable$parameter <- NA
# dailyDataAvailable2 <- merge(dailyDataAvailable, parameterQ[,c(1,3)], by = "parm_cd")
# siteINFO <- readNWISsite(siteNumber)
# siteAll <- readNWISdata(sites = siteNumber, service = "iv", startDate = startDate, endDate = endDate,tz = timezone)

#save(siteAll, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_11455315.RData"))

load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_11455315.RData"))

col2get <- data.frame(colnames(siteAll),NA)
col2get[,2] <- stringr::str_match(col2get[,1], "_\\d+")
col2get$parm_cd <- substr(col2get[,2],2,nchar(col2get[,2]))
colnames(col2get) <- c("colsNames","num1","parm_cd")
col2get2 <- merge(col2get,parameterQ[,c(1,3)],by = "parm_cd")

df_Liberty <- siteAll[,c(2,3,12,13,# 12 and 13 are DO and its QC status
                         which(colnames(siteAll) %in% col2get2[c(1,2, #temperature of upper sonde and its QC status
                                                                 8,7,# SC of upper sonde and its QC status
                                                                 13,14,# fdom of upper sonde and its QC status
                                                                 16,15,# chl of upper sonde and its QC status
                                                                 19,20,# turb of upper sonde and its QC status
                                                                 9,10,# pH and its QC status
                                                                 5,6) # gage height and its QC status
                                                               ,"colsNames"]
                               ))] 

col2get2$parm_nm
colnames(df_Liberty)[3:18] <- c("do","do_flag","tempC","tempC_flag","gage","gage_flag","sc","sc_flag","pH","pH_flag","fdom","fdom_flag","chl","chl_flag","turb","turb_flag")

save(df_Liberty, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_Liberty.RData"))
```

For 2023 data from USGS Toland station near Decker Island
```{r}
library(tidyverse)
library(dataRetrieval)
rm(list = ls())

siteNumber <- "11455485"
parameterCd <- "00065" # Discharge
startDate <- "2023-01-01T00:00"
endDate <- "2023-12-31T23:45"
timezone <- "America/Los_Angeles"

parameterQ <- read.csv(here::here("raw","ExtPrograms","USGS","USGS_parameters.csv"))

# dailyDataAvailable <- whatNWISdata(
#  siteNumber = siteNumber,
#  service = "iv"
# )
# dailyDataAvailable$parameter <- NA
# dailyDataAvailable2 <- merge(dailyDataAvailable, parameterQ[,c(1,3)], by = "parm_cd")
# siteINFO <- readNWISsite(siteNumber)
# siteAll <- readNWISdata(sites = siteNumber, service = "iv", startDate = startDate, endDate = endDate,tz = timezone)

#save(siteAll, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_11455485.RData"))

load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_11455485.RData"))

col2get <- data.frame(colnames(siteAll),NA)
col2get[,2] <- stringr::str_match(col2get[,1], "_\\d+")
col2get$parm_cd <- substr(col2get[,2],2,nchar(col2get[,2]))
colnames(col2get) <- c("colsNames","num1","parm_cd")
col2get2 <- merge(col2get,parameterQ[,c(1,3)],by = "parm_cd")

df_Toland <- siteAll[,c(2,3,14,15, # 14 and 15 are DO and its QC status
                        which(colnames(siteAll) %in% col2get2[c(3,4, #temperature of upper sonde and its QC status,
                                                                5,6, #gage height and its QC status
                                                                8,10,# SC of upper sonde and its QC status
                                                                11,12, # pH and its QC status
                                                                13,14,# fdom of upper sonde and its QC status
                                                                15,16,# chl of upper sonde and its QC status
                                                                17,18) # turb of upper sonde and its QC status
                                                              ,"colsNames"] 
                              ))] 

col2get2$parm_nm
colnames(df_Toland)[3:18] <- c("do","do_flag","tempC","tempC_flag","gage","gage_flage","sc","sc_flag","pH","pH_flag","fdom","fdom_flag","chl","chl_flag","turb","turb_flag")

save(df_Toland, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_Toland.RData"))
```

For 2023 data from USGS Van Sickle station near Winter Island
```{r}
library(tidyverse)
library(dataRetrieval)
rm(list = ls())

siteNumber <- "11455508"
parameterCd <- "00065" # Discharge
startDate <- "2023-01-01T00:00"
endDate <- "2023-12-31T23:45"
timezone <- "America/Los_Angeles"

parameterQ <- read.csv(here::here("raw","ExtPrograms","USGS","USGS_parameters.csv"))

# dailyDataAvailable <- whatNWISdata(
#  siteNumber = siteNumber,
#  service = "iv"
# )
# dailyDataAvailable$parameter <- NA
# dailyDataAvailable2 <- merge(dailyDataAvailable, parameterQ[,c(1,3)], by = "parm_cd")
# siteINFO <- readNWISsite(siteNumber)
# siteAll <- readNWISdata(sites = siteNumber, service = "iv", startDate = startDate, endDate = endDate,tz = timezone)

#save(siteAll, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_11455508.RData"))

load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_11455140.RData"))

col2get <- data.frame(colnames(siteAll),NA)
col2get[,2] <- stringr::str_match(col2get[,1], "_\\d+")
col2get$parm_cd <- substr(col2get[,2],2,nchar(col2get[,2]))
colnames(col2get) <- c("colsNames","num1","parm_cd")
col2get2 <- merge(col2get,parameterQ[,c(1,3)],by = "parm_cd")

df_VanSickle <- siteAll[,c(2,3,12,13, # 12 and 13 are DO and its QC status
                          which(colnames(siteAll) %in% col2get2[c(1,2, #temperature of upper sonde and its QC status
                                                                  7,8,# SC of upper sonde and its QC status
                                                                  13,14,# fdom of upper sonde and its QC status
                                                                  16,15,# chl of upper sonde and its QC status
                                                                  17,18,# turb of upper sonde and its QC status
                                                                  9,10,# pH and its QC status
                                                                  5,6) # gage height and its QC status
                                                                ,"colsNames"] 
                                ))] 

col2get2$parm_nm
colnames(df_VanSickle)[3:18] <- c("do","do_flag","tempC","tempC_flag","gage","gage_flag","sc","sc_flag","pH","pH_flag","fdom","fdom_flag","chl","chl_flag","turb","turb_flag")

save(df_VanSickle, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_VanSickle.RData"))
```

For 2023 data from USGS Grizzly Bay station near Tule Red
```{r}
library(tidyverse)
library(dataRetrieval)
rm(list = ls())

siteNumber <- "380631122032201"
parameterCd <- "00065" # Discharge
startDate <- "2023-01-01T00:00"
endDate <- "2023-12-31T23:45"
timezone <- "America/Los_Angeles"

parameterQ <- read.csv(here::here("raw","ExtPrograms","USGS","USGS_parameters.csv"))

# dailyDataAvailable <- whatNWISdata(
#  siteNumber = siteNumber,
#  service = "iv"
# )
# dailyDataAvailable$parameter <- NA
# dailyDataAvailable2 <- merge(dailyDataAvailable, parameterQ[,c(1,3)], by = "parm_cd")
# siteINFO <- readNWISsite(siteNumber)
# siteAll <- readNWISdata(sites = siteNumber, service = "iv", startDate = startDate, endDate = endDate,tz = timezone)

#save(siteAll, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_380631122032201.RData"))

load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_380631122032201.RData"))

col2get <- data.frame(colnames(siteAll),NA)
col2get[,2] <- stringr::str_match(col2get[,1], "_\\d+")
col2get$parm_cd <- substr(col2get[,2],2,nchar(col2get[,2]))
colnames(col2get) <- c("colsNames","num1","parm_cd")
col2get2 <- merge(col2get,parameterQ[,c(1,3)],by = "parm_cd")

df_Grizzly <- siteAll[,c(2,3,8,9, # 8 and 9 are DO and its QC status
                         which(colnames(siteAll) %in% col2get2[c(2,1, #temperature of upper sonde and its QC status
                                                                 3,4,# SC of upper sonde and its QC status
                                                                 10,9,# fdom of upper sonde and its QC status
                                                                 11,12,# chl of upper sonde and its QC status
                                                                 14,13,# turb of upper sonde and its QC status
                                                                 6,5)# pH and its QC status
                                                               ,"colsNames"]
                               ))] 

col2get2$parm_nm
colnames(df_Grizzly)[3:16] <- c("do","do_flag","tempC","tempC_flag","sc","sc_flag","pH","pH_flag","fdom","fdom_flag","chl","chl_flag","turb","turb_flag")

save(df_Grizzly, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_Grizzly.RData"))
```


For 2023 data from USGS Rush Ranch station near Wings
```{r}
library(tidyverse)
library(dataRetrieval)
rm(list = ls())

siteNumber <- "381142122015801"
parameterCd <- "00065" # Discharge
startDate <- "2023-01-01T00:00"
endDate <- "2023-12-31T23:45"
timezone <- "America/Los_Angeles"

parameterQ <- read.csv(here::here("raw","ExtPrograms","USGS","USGS_parameters.csv"))

# dailyDataAvailable <- whatNWISdata(
#  siteNumber = siteNumber,
#  service = "iv"
# )
# dailyDataAvailable$parameter <- NA
# dailyDataAvailable2 <- merge(dailyDataAvailable, parameterQ[,c(1,3)], by = "parm_cd")
# siteINFO <- readNWISsite(siteNumber)
# siteAll <- readNWISdata(sites = siteNumber, service = "iv", startDate = startDate, endDate = endDate,tz = timezone)

#save(siteAll, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_381142122015801.RData"))

load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_381142122015801.RData"))

col2get <- data.frame(colnames(siteAll),NA)
col2get[,2] <- stringr::str_match(col2get[,1], "_\\d+")
col2get$parm_cd <- substr(col2get[,2],2,nchar(col2get[,2]))
colnames(col2get) <- c("colsNames","num1","parm_cd")
col2get2 <- merge(col2get,parameterQ[,c(1,3)],by = "parm_cd")

df_RushRanch <- siteAll[,c(2,3,12,13, # 12 and 13 are DO and its QC status
                         which(colnames(siteAll) %in% col2get2[c(1,2, #temperature of upper sonde and its QC status
                                                                 8,7,# SC of upper sonde and its QC status
                                                                 13,14,# fdom of upper sonde and its QC status
                                                                 16,15,# chl of upper sonde and its QC status
                                                                 17,18,# turb of upper sonde and its QC status
                                                                 9,10,# pH and its QC status
                                                                 5,6)# gage height and its QC status
                                                               ,"colsNames"]
                               ))] 

col2get2$parm_nm
colnames(df_RushRanch)[3:18] <- c("do","do_flag","tempC","tempC_flag","gage","gage_flag","sc","sc_flag","pH","pH_flag","fdom","fdom_flag","chl","chl_flag","turb","turb_flag")

save(df_RushRanch, file = here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_RushRanch.RData"))
```

For 2023 data from DWR Beldens station near Wings
```{r}
library(tidyverse)
library(CDECRetrieve)
rm(list = ls())

BDL_DO <- cdec_query("BDL", "61", "E", "2023-01-01", "2023-12-31")
BDL_temp <- cdec_query("BDL", "25", "E", "2023-01-01", "2023-12-31")
BDL_sc <- cdec_query("BDL", "100", "E", "2023-01-01", "2023-12-31")
BDL_chl <- cdec_query("BDL", "28", "E", "2023-01-01", "2023-12-31")
BDL_ph <- cdec_query("BDL", "62", "E", "2023-01-01", "2023-12-31")
BDL_turb <- cdec_query("BDL", "27", "E", "2023-01-01", "2023-12-31")

#save(BDL_DO, BDL_temp, BDL_sc, BDL_chl, BDL_ph, BDL_turb, file = here::here("working", "ExtPrograms", "ExtProg_2023", "DWR_BDL.RData"))
#load(here::here("working", "ExtPrograms", "ExtProg_2023", "DWR_BDL.RData"))

BDL_DO$do <- as.numeric(BDL_DO$parameter_value)
BDL_temp$tempC <- (as.numeric(BDL_temp$parameter_value)-32)*5/9
BDL_sc$sc <- as.numeric(BDL_sc$parameter_value)
BDL_chl$chl <- as.numeric(BDL_chl$parameter_value)
BDL_turb$turb <- as.numeric(BDL_turb$parameter_value)
BDL_ph$ph <- as.numeric(BDL_ph$parameter_value)

df_Beldens <- cbind.data.frame(BDL_DO[,c("location_id","datetime","do")],
                           BDL_temp[,c("tempC")],
                           BDL_sc[,c("sc")],
                           BDL_chl[,c("chl")],
                           BDL_turb[,c("turb")],
                           BDL_ph[,c("ph")])

colnames(df_Beldens) <- c("site_no","dateTime","do","tempC","sc","chl","turb","pH")

df_Beldens$do_flag <- "P"
df_Beldens$tempC_flag <- "P"
df_Beldens$sc_flag <- "P"
df_Beldens$chl_flag <- "P"
df_Beldens$turb_flag <- "P"
df_Beldens$pH_flag <- "P"

save(df_Beldens, file = here::here("working", "ExtPrograms", "ExtProg_2023", "DWR_Beldens.RData"))
```

Check the coverage of Accepted vs Provisional data
```{r}
library(ggplot2)
library(ggpubr)
rm(list = ls())

load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_ToeDrain.RData"))
load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_Liberty.RData"))
load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_Toland.RData"))
load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_VanSickle.RData"))
load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_Grizzly.RData"))
load(here::here("working", "ExtPrograms", "ExtProg_2023", "USGS_RushRanch.RData"))
load(here::here("working", "ExtPrograms", "ExtProg_2023", "DWR_Beldens.RData"))

list_all <- list(df_ToeDrain, df_Liberty, df_Toland, df_VanSickle, df_RushRanch, df_Grizzly, df_Beldens)
names(list_all) <- c("Toe Drain","Liberty Island","Toland Landing", "Van Sickle", "Rush Ranch", "Grizzly Bay", "Beldens Landing")

dat2subset <- c("dateTime","do","tempC","sc","pH","fdom","chl","turb")
flag2subset <- c("dateTime","do_flag","tempC_flag","sc_flag","pH_flag","fdom_flag","chl_flag","turb_flag")

list_long <- list()
list_plo <- list()
for(i in 1:length(list_all)){
        df_longData <- reshape2::melt(list_all[[i]][,colnames(list_all[[i]]) %in% dat2subset], id.vars = c("dateTime"))
        df_longQC <- reshape2::melt(list_all[[i]][,colnames(list_all[[i]]) %in% flag2subset], id.vars = c("dateTime"))
        
        df_long <- cbind.data.frame(df_longData, df_longQC[,3])
        colnames(df_long)[4] <- "flag"
        ploX <- ggplot(df_long[which(df_long$flag %in% c("A","P")),], aes(x = dateTime, y = value)) +
                geom_point(aes(color = flag)) +
                facet_grid(variable ~., scales = "free") +
                ggtitle(names(list_all)[[i]])
        list_long[[i]] <- df_long
        list_plo[[i]] <- ploX
}
names(list_plo) <- names(list_all)
names(list_long) <- names(list_all)
multi_plo <- ggarrange(list_plo[[1]], list_plo[[2]], list_plo[[3]], list_plo[[4]], list_plo[[5]], list_plo[[6]], list_plo[[7]],
                         ncol = 7, nrow = 1,
                         common.legend = FALSE, legend = "bottom")
ggsave(paste("ExtPrograms_2023",".png",sep = ""), multi_plo, width = 1920, height = 1080, dpi = 150, units = "px", path = here::here("working","ExtPrograms","ExtProg_2023"))

save(list_all,list_long, file = here::here("working","ExtPrograms", "ExtProg_2023","AllExtProgram.RData"))
```


