---
title: "FRP_ContinuousWQ_SondeWorksheets"
author: "DMC"
date: "6/23/2023"
output: html_document
---

The goal of this file is to import worksheets from Survey123 and make RData files to use in the Processing script

First, we'll import the Exchange Worksheets and their crosswalk (these were generated using the first version of the CDFW Survey123 e-forms)
```{r}
rm(list = ls())

# read in the crosswalk file for renaming columns of raw Survey123 export file (Must make sure version matches)
cw_Exch <- data.frame(read.csv(here::here("raw","Survey123", "Exchanges_v230630", "Exchanges230630_ColumnCrosswalk.csv")))

# read in the export frile from Survey123
#df_Exch <- data.frame(read.csv(here::here("raw","Survey123", "Exchanges230630_Export230703.csv"))) # this is for an older version now stored in the 'archive' folder
df_Exch <- data.frame(read.csv(here::here("raw","Survey123", "Exchanges_v230630", "Exchanges230630_Export240602.csv")))

# rename the columns of the export data
colnames(df_Exch) <- cw_Exch$Var_Name

# make a date variable that is in local timezone
df_Exch$date2 <- as.Date(format(lubridate::mdy_hms(df_Exch$exchange_date), tz = "UTC"))


### make datetime variable for the individual measurements
# first, we will subset all columns with time in name
df_ExchTimes <- df_Exch[,stringr::str_detect(colnames(df_Exch), "_time")]
# attach the new date object to subset
df_ExchTimes2 <- cbind(df_ExchTimes, data.frame(date2 = df_Exch$date2))
# make a blank version of subset to repopulate with datetime objects
df_ExchTimes3 <- df_ExchTimes
df_ExchTimes3[,] <- NA
# populate blank version of subset with newly created datetime objects
for(i in 1:ncol(df_ExchTimes3)){
  df_ExchTimes3[,i] = as.POSIXct(strptime(paste(as.character(df_ExchTimes2[,"date2"]),df_ExchTimes[,i],sep = " "), format = "%Y-%m-%d %H:%M"), tz = "UTC")
}
# populate the original exchange dataset with the newly created datetime objects
for(i in 1:ncol(df_ExchTimes3)){
  for(j in 1:ncol(df_Exch)){
    if(colnames(df_ExchTimes3)[i] == colnames(df_Exch)[j]){
      df_Exch[,j] = df_ExchTimes3[,i]
    }
  }
}

# make simple subsets of deployment/recovery times. These will be used for trimming datasets based on time
df_DeployTimes <- df_Exch[,c("station","date2","deployed_sonde_id","deployment_start_time","departure_time")]
df_RecoveryTimes <- df_Exch[,c("station","date2","recovered_sonde_id","recovery_stop_time","arrival_time")]
df_Times <- df_Exch[,c("station","date2","deployed_sonde_id","deployment_start_time","departure_time","recovered_sonde_id","recovery_stop_time","arrival_time")]

df_TimesLong <- rbind.data.frame(data.frame(action = c("Recovered"),
                                            sondeID = df_RecoveryTimes$recovered_sonde_id,
                                            timeX = df_RecoveryTimes$arrival_time,
                                            dateX = df_RecoveryTimes$date2),
                                 data.frame(action = c("Deployed"),
                                            sondeID = df_DeployTimes$deployed_sonde_id,
                                            timeX = df_DeployTimes$departure_time,
                                            dateX = df_DeployTimes$date2)
                                 )
df_TimesLong$sonde_date <- paste(df_TimesLong$sondeID,
                                 df_TimesLong$dateX,
                                 sep = " ")
# make a new variable to match with the raw data in downstream processes

df_DeployTimes$sonde_dateDeploy <- paste(df_DeployTimes$deployed_sonde_id,
                                   df_DeployTimes$date2,
                                   sep = " ")
df_RecoveryTimes$sonde_dateRecov <- paste(df_RecoveryTimes$recovered_sonde_id,
                                     df_RecoveryTimes$date2,
                                     sep = " ")

# force date change of recovery date for the two deployments since the battery died prior to recovery. This step allows for further matching downstream
df_RecoveryTimes$date2[which(df_RecoveryTimes$station == "FLYW_Bifurcation" & df_RecoveryTimes$recovered_sonde_id == "19C101554" & as.character(df_RecoveryTimes$date2) == "2022-09-22")] <- as.Date("2022-08-21", format = "%Y-%m-%d")
df_RecoveryTimes$date2[which(df_RecoveryTimes$station == "FLYW_Bifurcation" & df_RecoveryTimes$recovered_sonde_id == "19C101551" & as.character(df_RecoveryTimes$date2) == "2022-10-24")] <- as.Date("2022-10-23", format = "%Y-%m-%d")
# force date change of recovery date for the two deployments since the battery died prior to recovery. This step allows for further matching downstream
df_Exch$date2[which(df_Exch$station == "FLYW_Bifurcation" & df_Exch$recovered_sonde_id == "19C101554" & as.character(df_Exch$date2) == "2022-09-22")] <- as.Date("2022-08-21", format = "%Y-%m-%d")
df_Exch$date2[which(df_Exch$station == "FLYW_Bifurcation" & df_Exch$recovered_sonde_id == "19C101551" & as.character(df_Exch$date2) == "2022-10-24")] <- as.Date("2022-10-23", format = "%Y-%m-%d")

#testTime <- data.frame(origTime = df_Exch$exchange_date, newTime = NA)
#testTime$newTime <- lubridate::mdy_hms(testTime$origTime)
#testTime$pacTime <- format(testTime$newTime, tz = "UTC")
#testTime$pacDate <- as.Date(testTime$pacTime)

# save the exchange times for use in 'ContinuousSonde_Processing.Rmd'
save(df_DeployTimes, df_RecoveryTimes, file = here::here("working","CDFW_ExchangeTimes.RData"))
# save the exchange worksheet for use in 'ErrorCalculations.Rmd'
save(df_Exch, file = here::here("working","CDFW_ExchangeWorksheet.RData"))
```

Now, let's import the Calibration Worksheets and their crosswalk (these were generated using the first version of the CDFW Survey123 e-forms)
```{r}
rm(list = ls())
'%ni%' = Negate('%in%')
cw_Calib <- data.frame(read.csv(here::here("raw","Survey123", "Calibrations_v230612", "Calibration230612_ColumnCrosswalk.csv")))
#df_Calib <- data.frame(read.csv(here::here("raw","Survey123", "Calibrations_v230612", "Calibration230612_Export230706.csv"))) # this is for an older version now stored in the 'archive' folder
df_Calib <- data.frame(read.csv(here::here("raw","Survey123", "Calibrations_v230612", "Calibration230612_Export240206.csv")))
colnames(df_Calib) <- cw_Calib$Var_Name

# make a datetime object for the deployment start/stop time
df_Calib$dts_startstop <- format(lubridate::mdy_hms(df_Calib$deployment_startstop_time), tz = "UTC")

# make 2 separate dataframes (1 with just the data we are interested and 1 with the metadata)
df_CalibData <- df_Calib[,c("GlobalID","sonde_id","sonde_other","discrete_or_continuous","pre_post","dts_startstop",colnames(df_Calib)[53:95])]
df_CalibMeta <- df_Calib[,c("GlobalID","sonde_id","sonde_other","discrete_or_continuous","pre_post","dts_startstop",colnames(df_Calib)[7:52])]

save(df_Calib, df_CalibData, df_CalibMeta, file = here::here("working","CDFW_CalibrationWorksheet.RData"))
```

This chunk contains the crosswalk for DWR's sonde names and their corresponding sonde ID (i.e., serial number). Grabbed from the 'Master_LabInventory_BothLabs.xlsx' file in DWR's Water Quality Lab SharePoint
```{r DWR sonde name crosswalk}
library(readxl)

rm(list = ls())
'%ni%' = Negate('%in%')

DWR_sondeID <- read_excel(here::here("Raw","Master_LabInventory_BothLabs.xlsx"), sheet = "Sonde Serial #s", col_types = c("text","text"))
colnames(DWR_sondeID) <- c("sonde_id","SondeName")
DWR_sondeID <- rbind.data.frame(DWR_sondeID, data.frame(sonde_id = "14J104011", SondeName = "Chamberlain"))


save(DWR_sondeID, file = here::here("working","DWR_SondeID_crosswalk.Rda"))
```


This chunk imports the "SondeData_StartStopTimes.xlsx" from the DWR Water Quality Lab's SharePoint.
```{r DWR start/stop times}
library(readxl)

rm(list = ls())
'%ni%' = Negate('%in%')

s <- excel_sheets(here::here("Raw","SondeData_StartStopTimes.xlsx"))
s2 <- s[-1]
list_s <- list()
for(i in seq_along(s2)){
  df <- read_excel(here::here("Raw","SondeData_StartStopTimes.xlsx"), sheet = s2[i], skip = 1, col_types = c("text","date",rep("text",8)))
  list_s[[i]] <- df
  rm(df)
}

SS <- do.call(rbind.data.frame, list_s)

### There are some difficulties with the time columns so will standardize them for operability
# First, convert to numeric and force NAs in rows that dont have numbers
SS$start1 <- as.numeric(SS$`Start time`)
SS$end1 <- as.numeric(SS$`end time`)

# Look for early hours (before 10am) and add a colon
SS$start2 <- ifelse(SS$start1 > 1 & SS$start1 <= 999,
                    as.character(paste0(substr(SS$start1,0,1),":",substr(SS$start1,2,3))),
                    NA)
# Look for later hours (after 10am) and add a colon
SS$start2 <- ifelse(SS$start1 > 999 & is.na(SS$start2)==T,
                    as.character(paste0(substr(SS$start1,0,2),":",substr(SS$start1,3,4))),
                    SS$start2)
# Look for early hours (before 10am) and add a colon
SS$end2 <- ifelse(SS$end1 > 1 & SS$end1 <= 999,
                    as.character(paste0(substr(SS$end1,0,1),":",substr(SS$end1,2,3))),
                    NA)
# Look for later hours (after 10am) and add a colon
SS$end2 <- ifelse(SS$end1 > 999 & is.na(SS$end2)==T,
                    as.character(paste0(substr(SS$end1,0,2),":",substr(SS$end1,3,4))),
                    SS$end2)

### Some rows had HH:MM:SS in the excel file and that imported incorrectly
# Manually add the times
SS$start2[which(SS$Station=="TRC" & SS$Date == as.Date("2022-12-29"))] <- "11:43"
SS$end2[which(SS$Station=="TRC" & SS$Date == as.Date("2022-12-29"))] <- "10:43"
SS$start2[which(SS$Station=="WNG" & SS$Date == as.Date("2023-06-20"))] <- "14:00"
SS$end2[which(SS$Station=="WNG" & SS$Date == as.Date("2023-06-20"))] <- "13:15"

### Add the sonde ID to the data frame using the DWR sonde name crosswalk made in previous chunk
load(here::here("working","DWR_SondeID_crosswalk.Rda"))
SS.2 <- merge(SS, DWR_sondeID, by.x = "Installed Sonde", by.y = "SondeName", all.x = T)
SS.2$sonde_id[which(SS.2$`Installed Sonde` == "19C101658")] <- "19C101658"

SS.2$departure_time <- as.POSIXct(strptime(paste(as.character(SS.2$Date),SS.2$start2, sep = " "),
                                           format = "%Y-%m-%d %H:%M", tz = "UTC"))
SS.2$arrival_time <- as.POSIXct(strptime(paste(as.character(SS.2$Date),SS.2$end2, sep = " "),
                                         format = "%Y-%m-%d %H:%M", tz = "UTC"))

DWR.startstop <- SS.2[which(is.na(SS.2$sonde_id)==F & is.na(SS.2$departure_time)==F & is.na(SS.2$arrival_time)==F),
                      c("sonde_id","departure_time","arrival_time","end2")]
save(DWR.startstop, file = here::here("working","DWR_startstop.Rda"))
```

This chunk reads in all of the Drift Error Calculation Worksheets for DWR deployments that are stored on the SharePoint site. This replaces the need for DWR_transcribed_ErrorRatings.Rmd
```{r}
rm(list = ls())
# Load in the crosswalk between DWR naming scheme and SondeID
load(here::here("working","DWR_SondeID_crosswalk.Rda"))
# Add one more line since there is one Worksheet with CDFW as the informal name
DWR_sondeID <- rbind.data.frame(DWR_sondeID,
                                data.frame(sonde_id = "19C101659",
                                           SondeName = "CDFW"))
# Make lists to store each individual portion of the worksheet
list_all_foul <- list() # fouling data
list_all_drift <- list() # sensor drift data
list_all_meta <- list() # metadata
list_all_names <- list() # names to later store each list with

# Make a vector with each file name
files2import <- list.files(here::here("raw","DWR_errorcalcs"))

# This for loop imports 1 Worksheet three different times so that the pertinent information is stored correctly. This is required since the Excel file is not very well designed for R import
for(i in 1:length(files2import)){
  # import the fouling section
  foul <- data.frame(readxl::read_xlsx(paste(here::here("raw","DWR_errorcalcs"),files2import[i], sep = "/"), range = c("D12:I18"), col_names = F))
  # rename the columns
  colnames(foul) <- c("varX","units","preclean_deployed","preclean_verif","postclean_deployed","postclean_verif")
  # remove empty rows
  foul.2 <- foul[-c(4,7),]
  # store fouling data frame as list item
  list_all_foul[[i]] <- foul.2
  
  # import the sensor drift section
  drift <- data.frame(readxl::read_xlsx(paste(here::here("raw","DWR_errorcalcs"),files2import[i], sep = "/"), range = c("D22:G29"), col_names = F))
  # rename the columns
  colnames(drift) <- c("varX","units","standard","sonde")
  # remove the empty row
  drift.2 <- drift[-c(4),]
  # fill in empty cells
  drift.2$varX[c(4:7)] <- c("ph_7","ph_10","turb_low","turb_high")
  drift.2$units[which(drift.2$varX == "ph_10")] <- "Units"
  drift.2$units[which(drift.2$varX == "turb_high")] <- "NTU"
  # store sensor drift data as list item
  list_all_drift[[i]] <- drift.2
  
  # import metadata section
  meta <- data.frame(readxl::read_excel(paste(here::here("raw","DWR_errorcalcs"),files2import[i], sep = "/"), range = c("M10:O19"), col_names = F))
  # rename columns
  colnames(meta) <- c("meta_variable","remove","meta_value")
  # remove empty columns and rows
  meta.2 <- meta[-c(7),-c(2)]
  # fix the date
  meta.2$dateFix <- as.numeric(meta.2$meta_value)
  # fix the date part2
  meta.2$dateTime <- meta.2$dateFix
  # fix the date part3
  meta.2$dateTime[which(meta.2$meta_variable== "Field Date:")] <- paste(as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Field Date:")])+ as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Exchange Time:")]))
  meta.2$dateTime[which(meta.2$meta_variable== "Post-Deployment Date:")] <- paste(as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Post-Deployment Date:")])+ as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Post-Deployment Time:")]))
  # fix the date part4
  meta.2$dts <- round(as.POSIXct(as.numeric(meta.2$dateTime) * (60 * 60 * 24), origin = "1899-12-30", tz = "UTC"), units = c("mins"))
  # remove old date fix columns and unnecessary rows that store Time
  meta.3 <- meta.2[-c(6,8),-which(colnames(meta.2) %in% c("dateFix","dateTime"))]
  # replace the poorly formatted Excel date with R preferred date
  meta.3$meta_value[which(meta.3$meta_variable == "Field Date:")] <- substr(as.character(meta.3$dts[which(meta.3$meta_variable == "Field Date:")]),0,19)
  meta.3$meta_value[which(meta.3$meta_variable == "Post-Deployment Date:")] <- substr(as.character(meta.3$dts[which(meta.3$meta_variable == "Post-Deployment Date:")]),0,19)
  # remove the old date column
  meta.4 <- meta.3[,-which(colnames(meta.3) %in% c("dts"))]
  # store  metadata as a list item
  list_all_meta[[i]] <- meta.4
  
  # make a data frame that holds info to name each list item
  df_name <- data.frame(sondename = meta.4$meta_value[which(meta.4$meta_variable == "Sonde ID:")],
                        station = meta.4$meta_value[which(meta.4$meta_variable == "Removed From:")],
                        date_recovery = substr(meta.4$meta_value[which(meta.4$meta_variable == "Field Date:")],0,10),
                        sondeID = NA)
  # determine sondeID for each line based on matching informal name
  df_name$sondeID <- DWR_sondeID$sonde_id[which(df_name$sondename == DWR_sondeID$SondeName)]
  # store naming info as a list item
  list_all_names[[i]] <- df_name

  # remove temporary items
  rm(foul, foul.2, drift, drift.2, meta, meta.2, meta.3, meta.4, df_name)
}

# make long data frame from the list_all_names
df_names <- do.call(rbind.data.frame, list_all_names)
# fix incorrect dates (had to look at list_all_meta and find the corresponding item and then open that Excel file)
df_names$date_recovery[which(df_names$sondeID == "21L101256" & df_names$date_recovery == "0")] <- "2022-06-30" # was missing Exchange Time so the date was set to 0
df_names$date_recovery[which(df_names$sondeID == "23H107030" & df_names$date_recovery == "0")] <- "2023-11-21" # was missing Exchange Time so the date was set to 0
df_names$date_recovery[which(df_names$sondeID == "19C101658" & df_names$date_recovery == "2024-06-01")] <- "2021-08-26" # was missing Exchange Time so the date was set to 0

# set the names for each item in each list
names(list_all_foul) <- paste(df_names$sondeID, df_names$date_recovery, sep = " ")
names(list_all_drift) <- paste(df_names$sondeID, df_names$date_recovery, sep = " ")
names(list_all_meta) <- paste(df_names$sondeID, df_names$date_recovery, sep = " ")

save(list_all_foul, list_all_drift, list_all_meta, file = here::here("working","DWR_ErrorWorksheets.RData"))

# foul <- readxl::read_xlsx(here::here("raw","2023-04-06_DRIFT_Wings.xlsx"), range = c("D12:I18"), col_names = F)
# drift <- readxl::read_xlsx(here::here("raw","2023-04-06_DRIFT_Wings.xlsx"), range = c("D22:G29"), col_names = F)
# meta <- readxl::read_excel(here::here("raw","2023-04-06_DRIFT_Wings.xlsx"), range = c("M10:O19"), col_names = F)
# 
# colnames(foul) <- c("varX","units","preclean_deployed","preclean_verif","postclean_deployed","postclean_verif")
# foul.2 <- foul[-c(4,7),]
# 
# colnames(drift) <- c("varX","units","standard","sonde")
# drift.2 <- drift[-c(4),]
# drift.2$varX[c(4:7)] <- c("ph_7","ph_10","turb_low","turb_high")
# drift.2$units[which(drift.2$varX == "ph_10")] <- "Units"
# drift.2$units[which(drift.2$varX == "turb_high")] <- "NTU"
# 
# colnames(meta) <- c("meta_variable","remove","meta_value")
# meta.2 <- meta[-c(7),-c(2)]
# meta.2$dateFix <- as.numeric(meta.2$meta_value)
# meta.2$dateTime <- meta.2$dateFix
# meta.2$dateTime[which(meta.2$meta_variable== "Field Date:")] <- paste(as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Field Date:")])+ as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Exchange Time:")]))
# meta.2$dateTime[which(meta.2$meta_variable== "Post-Deployment Date:")] <- paste(as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Post-Deployment Date:")])+ as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Post-Deployment Time:")]))
# #meta.2$meta_value[which(meta.2$meta_variable== "Field Date:")] <- as.Date(as.numeric(meta.2$meta_value[which(meta.2$meta_variable== "Field Date:")]), origin = "1900-01-01")
# #meta.2$dateFix2 <- as.Date(as.numeric(meta.2$dateFix), origin = "1899-12-30")
# meta.2$dts <- as.POSIXct(as.numeric(meta.2$dateTime) * (60 * 60 * 24), origin = "1899-12-30", tz = "UTC")
# 
# meta.3 <- meta.2[-c(6,8),-which(colnames(meta.2) %in% c("dateFix","dateTime"))]
# meta.3$meta_value[which(meta.3$meta_variable == "Field Date:")] <- substr(as.character(meta.3$dts[which(meta.3$meta_variable == "Field Date:")]),0,19)
# meta.3$meta_value[which(meta.3$meta_variable == "Post-Deployment Date:")] <- substr(as.character(meta.3$dts[which(meta.3$meta_variable == "Post-Deployment Date:")]),0,19)
# 
# meta.4 <- meta.3[,-which(colnames(meta.3) %in% c("dts"))]
```

